---
title: "Beboto vaccination coverage survey"
output: 
  word_document:
    keep_md: true
---

## Installing and loading required packages 

<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// setup \\\
-------------------------------------------------------------------------------->

```{r setup, include = FALSE, results='hide', message=FALSE, warning=FALSE}
## hide all code chunks in the output, but show errors
knitr::opts_chunk$set(echo = FALSE, error = TRUE, fig.width = 6*1.25, fig.height = 6)


## set default NA to - in output, define figure width/height
options(knitr.kable.NA = "-")


## Installing required packages for this template
required_packages <- c("knitr",       # create output docs
                       "here",        # find your files
                       "rio",         # for importing data
                       "epitrix",     # clean/shape data
                       "dplyr",       # clean/shape data
                       "tidyr",       # clean/shape data
                       "forcats",     # manipulate and rearrange factors
                       "stringr",     # manipulate texts
                       "ggplot2",     # create plots and charts
                       "sitrep",      # MSF field epi functions
                       "survey",      # for survey functions
                       "srvyr"        # dplyr wrapper for survey package
                       )

for (pkg in required_packages) {
  ## install packages if not already present
  if (!pkg %in% rownames(installed.packages())) {
    install.packages(pkg)
  }
  
  ## load packages to this current session 
  library(pkg, character.only = TRUE)
}


## set default text size to 18 for plots
## give classic black/white axes for plots
ggplot2::theme_set(theme_classic(base_size = 18))


```

<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// read_data \\\
--------------------------------------------------------------------------------
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r read_data  merge data, warning = FALSE, message = FALSE}

## Excel file ------------------------------------------------------------------

## read in household data sheet
study_data_hh <- rio::import(here::here("7.analysis", "data", "vaccination_coverage_cleaned.xlsx"), 
                             which = "hh level", na = ".")

## read in individual level data sheet
study_data_indiv <- rio::import(here::here("7.analysis", "data", "vaccination_coverage_cleaned.xlsx"), 
                                which = "ind level", na = ".")

## join the individual and household data to form a complete data set
study_data_raw <- left_join(study_data_hh, study_data_indiv, by = "merge_id")

## make a copy of your orginal dataset and name it study_data_cleaned
study_data_cleaned <- study_data_raw

```

<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// read_population_data \\\
--------------------------------------------------------------------------------
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r population_data, warning = FALSE, message = FALSE}

## Enter counts directly -------------------------------------------------------

#Enter population counts by groups. 

population_6m9y <- gen_population(
  groups = c("6 months-9 years"), 
  counts = c(24711), 
  strata = NULL) %>%
  rename (age_group = groups, 
          population = n)

```


```{r filtering for no children}

study_data_cleaned <- study_data_cleaned %>%
  filter(!is.na(child_number)) #filtering for no children, indicating no child of eligible age or no one home, etc.) 

```

```{r create_age_group}

## make sure age is an integer 
study_data_cleaned <- study_data_cleaned %>% 
  mutate(age_years = as.integer(age_years), 
         age_months = as.integer(age_months))

## create an age group variable, even though everyone in the dataset is all in one age group. 
study_data_cleaned <- study_data_cleaned %>%
mutate(age_group = factor(
    if(age_years >= 1) {
      "6m-9y"
    } else {
      "6m-9y"
    }
  ))

```


<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// browse_data \\\
--------------------------------------------------------------------------------
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r browse_data, eval = FALSE}

##Julia note: this is weird, it's returning ages that are fine (e.g. age of routine vaccination is 9 months and current age is 11 months. That's normal...)

## check for logical date inconsistencies 
## for example check vaccination age greater than current age and return corresponding IDs


study_data_cleaned$age_routine_vacc <- as.numeric(study_data_cleaned$age_routine_vacc)
study_data_cleaned$age_months <- as.numeric(study_data_cleaned$age_months)

study_data_raw %>% 
  filter(age_routine_vacc > age_months) %>%
  select("merge_id", "age_routine_vacc", "age_months")


```

<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// standardise_dates \\\
--------------------------------------------------------------------------------
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->


```{r standardise_dates}

## use the guess_dates() function to make a first pass at date variables.
study_data_cleaned <- study_data_cleaned %>%
   mutate_at(vars(matches("date|Date")), linelist::guess_dates,
             error_tolerance = 0.5)

#checked class of "today" date variable - it's character. 
class(study_data_cleaned$today)

#change "today" date variable to a date:
study_data_cleaned$today<- as.Date(study_data_cleaned$today, format = "%Y-%m-%d")

#drop data from training and pilot day. 
table(study_data_cleaned$today) # check which dates need to be dropped
#drop dates older than April 1, 2020
study_data_cleaned <- subset(study_data_cleaned, today >= "2020-04-01")

```

##RETURN to this later and do all the cleaning in R 


```{r cleaning}

#checked in excel to find weirdness for variables, like we did each day during survey. Corrected hh number, cluster number, and team number for some. 

#checking for weirdness here & corrected in excel if necessary
#any houshold marked as both first AND second visit on the same line. 
#table(study_data_cleaned$first_visit, study_data_cleaned$second_visit)

#any empty hh that gave consent
#table(study_data_cleaned$empty_household, study_data_cleaned$consent)

#remove space from ndaba3:
study_data_cleaned$village_name <- gsub(pattern = "ndaba 3",replacement = "ndaba3", study_data_cleaned$village_name)


#changed character variables that I'll be using to numeric: 
study_data_cleaned$children_count <- as.numeric(study_data_cleaned$children_count)
study_data_cleaned$cluster_number <- as.numeric(study_data_cleaned$cluster_number)
study_data_cleaned$household_number <- as.numeric(study_data_cleaned$household_number)

```

<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// remove_unused_data \\\
--------------------------------------------------------------------------------
It is important that you drop observations before adding survey weights!
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r remove_unused_data}

## store the cases that you drop so you can describe them (e.g. non-consenting)
dropped <- study_data_cleaned %>% 
  filter(consent =="no")

#drop the clusters used to replace the ferrick that was not accessible. Do not have population counts for those villages. 
dropped2 <- study_data_cleaned %>%
  filter(village_name == "other")

## drop the unused rows from the survey data set  
study_data_cleaned <- study_data_cleaned %>%
  filter(village_name != "other") %>%
  filter(consent == "yes")

## Drop columns ----------------------------------------------------------------
## OPTIONAL: This step shows you how you can remove certain variables.
## study_data_cleaned <- select(study_data_cleaned, -c("age_years", "sex"))

## OPTIONAL: if you want to inspect certain variables, you can select these by
## name or column number. This example creates a reduced dataset for the first
## three columns, age_years, and sex.

# study_data_reduced <- select(study_data_cleaned, c(1:3, "age_years", "sex")

```


<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// factor_vars \\\
--------------------------------------------------------------------------------
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r vaccination status}

## MSF vaccination - combine yes answers into one - yes card and yes verbal
study_data_cleaned <- study_data_cleaned %>% 
  mutate(msf_vacc_status = case_when(
    is.na(msf_vacc) ~ NA_character_,
    msf_vacc == "card" ~ "Yes", 
    msf_vacc == "verbal" ~ "Yes", 
    msf_vacc == "no" ~ "No", 
    msf_vacc == "dont_know" ~ "Don't know"))

#checking the variable we created above. 
table(study_data_cleaned$msf_vacc)
table(study_data_cleaned$msf_vacc_status)


## ROUTINE vaccination - combine yes answers into one - yes card and yes verbal
study_data_cleaned <- study_data_cleaned %>% 
  mutate(routine_vacc_status = case_when(
    is.na(routine_vacc) ~ NA_character_,
    routine_vacc == "card" ~ "Yes", 
    routine_vacc == "verbal" ~ "Yes", 
    routine_vacc == "no" ~ "No", 
    routine_vacc == "dont_know" ~ "Don't know", 
    routine_vacc == "no_answer" ~ "No answer"))

#checking the variable we created above.
table(study_data_cleaned$routine_vacc)
table(study_data_cleaned$routine_vacc_status)


## SIA vaccination - combine yes answers into one - yes card and yes verbal
study_data_cleaned <- study_data_cleaned %>% 
  mutate(sia_vacc_status = case_when(
    is.na(sia_vacc) ~ NA_character_,
    sia_vacc == "card" ~ "Yes", 
    sia_vacc == "verbal" ~ "Yes", 
    sia_vacc == "no" ~ "No", 
    sia_vacc == "dont_know" ~ "Don't know")) 

#checking the variable we created above.
table(study_data_cleaned$sia_vacc)
table(study_data_cleaned$sia_vacc_status)

## correct the order of levels in newly created variables:

#MSF vaccination
study_data_cleaned <- study_data_cleaned %>% 
  mutate(msf_vacc_status = fct_relevel(msf_vacc_status, 
                                       "Yes", 
                                       "No", 
                                       "Don't know"))

#ROUTINE vaccination
study_data_cleaned <- study_data_cleaned %>% 
  mutate(routine_vacc_status = fct_relevel(routine_vacc_status, 
                                       "Yes", 
                                       "No", 
                                       "Don't know", 
                                       "No answer"))

#SIA vaccination
study_data_cleaned <- study_data_cleaned %>% 
  mutate(sia_vacc_status = fct_relevel(sia_vacc_status, 
                                       "Yes", 
                                       "No", 
                                       "Don't know"))
```

<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// cluster_counts \\\
--------------------------------------------------------------------------------
You will need to have one column with a cluster identifier which 
matches your survey data, and another column with the number of households in 
each cluster. 
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r cluster_counts}

#read data in
cluster_counts <- rio::import(here::here("7.analysis", "data", "cluster counts.xlsx"))

#round digits
cluster_counts$total_hh<- round(cluster_counts$total_hh, digits = 0)

#lowercase
cluster_counts$village_name <- tolower(cluster_counts$village_name) 

#drop population column
cluster_counts <- cluster_counts %>%
    select(-pop)

#might need to be a tibble for code later? the template had this created as a tibble but I imported instead. 
as_tibble(cluster_counts)


```


<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// survey_weights \\\
--------------------------------------------------------------------------------
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r survey_weights, R TEMPLATE}

## merge village and household to create a unique household ID 
study_data_cleaned <- study_data_cleaned %>% 
  mutate(hh_id = str_glue("{village_name}_{household_number}"))

## create cluster weights 
#https://rdrr.io/github/R4EPI/sitrep/man/add_weights_cluster.html

study_data_cleaned <- add_weights_cluster(x = study_data_cleaned, 
                                          cl = cluster_counts, 
                                          eligible = children_count, 
                                          interviewed = children_count, 
                                          cluster_x = village_name, 
                                          cluster_cl = village_name, 
                                          household_x = household_number, 
                                          household_cl = total_hh, 
                                          surv_weight = "surv_weight_cluster", 
                                          surv_weight_ID = "surv_weight_ID_cluster", 
                                          ignore_cluster = FALSE, 
                                          ignore_household = FALSE)


```



<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// survey_design \\\
--------------------------------------------------------------------------------

Create survey object according to your study design. Used the same way as dataframes to calculate weight proportions etc. 
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r create_survey_design}

## cluster survey---------------------------------------------------------------------

survey_design <- study_data_cleaned %>% 
  as_survey_design(ids = cluster_number, # 1 for no cluster ids 
                   weights = surv_weight_cluster, # weight variable created above 
                   strata = NULL # sampling was simple (no strata)
                  )

```



<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// save_cleaned_data \\\
--------------------------------------------------------------------------------

You can save your cleaned dataset as an Excel. 
This automatically names your file "study_data_cleaned_DATE", where DATE is the
current date.
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r save_cleaned_data}
rio::export(study_data_cleaned, str_glue("study_data_cleaned_{Sys.Date()}_pk.xlsx"))
```



# Results

## Survey inclusion 


<!--~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// inclusion_counts \\\
--------------------------------------------------------------------------------

The below chunks calculate values that are displayed with the inline text

Get the counts of clusters and households included 
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~-->

```{r inclusion_counts}

## get counts of number of clusters 
num_clus <- study_data_cleaned %>%
  ## trim data to unique clusters
  distinct(cluster_number) %>% 
  ## get number of rows (count how many unique)
  nrow()

## get counts of number households 
num_hh <- study_data_cleaned %>% 
  ## get unique houses by cluster
  distinct(cluster_number, household_number) %>% 
  ## get number of rounds (count how many unique)
  nrow()

```


We included `r num_hh` households accross `r num_clus` clusters in this survey analysis. 


Among the `r nrow(dropped)` individuals without consent to participate in the survey, 
the reasons for refusal are ___________. 

<!--~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// cluster_hh_size \\\
--------------------------------------------------------------------------------

The below chunks calculate values that are displayed with the inline text

Get counts of households per cluster and individuals per household. 
From these create medians and standard deviations. 
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~-->

```{r cluster_hh_size}

## get counts of the number of households per cluster
clustersize <- study_data_cleaned %>% 
  ## trim data to only unique households within each cluster
  distinct(cluster_number, household_number) %>%
  ## count the number of households within each cluster
  count(cluster_number) %>% 
  pull(n)

## get the median number of households per cluster
clustermed <- median(clustersize)

## get the min and max number of households per cluster
## paste these together seperated by a dash 
clusterrange <- str_c(range(clustersize), collapse = "--")

## get counts of children per household 
## do this by cluster as household IDs are only unique within clusters
hhsize <- study_data_cleaned %>% 
  count(cluster_number, household_number) %>%
  pull(n) 

## get median number of children per household
hhmed <- median(hhsize)
## get the min and max number of children per household
## paste these together seperated by a dash 
hhrange <- str_c(range(hhsize), collapse = "--")

# get standard deviation 
hhsd <- round(sd(hhsize), digits = 1)
```


The median number of households per cluster was
`r clustermed`, with a range of `r clusterrange`. The median number of children
per household was `r hhmed` (range: `r hhrange`, standard deviation: `r hhsd`). 


## Demographic information


In total we included `r nrow(study_data_cleaned)` children in the survey analysis. 
The age breakdown and a comparison with the source population is shown below. 


<!--~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// median_age_sex_ratios \\\
--------------------------------------------------------------------------------

The below chunk calculate values that are displayed inline

This returns the median age and sex ratios overall as well as by age group. 
It also pulls the age group with the highest sex ratio. 

~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~-->

```{r median_age_sex_ratios}
## compute the median age 
medage <- median(study_data_cleaned$age_years)

## paste the lower and uper quartile together
iqr <- str_c(  # basically copy paste together the following
  ## calculate the 25% and 75% of distribution, with missings removed
  quantile(     
    study_data_cleaned$age_years, 
    c(0.25, 0.75), 
    na.rm = TRUE), 
  ## between lower and upper place an en-dash
  collapse = "--")


## compute overall sex ratio 
sex_ratio <- study_data_cleaned %>% 
  count(sex) %>%
  pivot_wider(names_from = sex, values_from = n) %>% 
  mutate(ratio = round(male/female, digits = 3)) %>%
  pull(ratio)

## compute sex ratios by age group 
# sex_ratio_age <- study_data_cleaned %>% 
#   count(age_group, sex) %>% 
#   pivot_wider(names_from = sex, values_from = n) %>% 
#   mutate(ratio = round(male/female, digits = 3)) %>%
#   select(age_group, ratio)

## sort table by ascending ratio then select the lowest (first)
# min_sex_ratio_age <- arrange(sex_ratio_age, ratio) %>% slice(1)
```

Among the `r nrow(study_data_cleaned)` surveyed individuals, there were 
`r fmt_count(study_data_cleaned, sex == "Female")` females and 
`r fmt_count(study_data_cleaned, sex == "Male")` males (unweighted). The male to
female ratio was `r sex_ratio` in the surveyed population. The lowest male to
female ratio was `r min_sex_ratio_age$ratio`
in the `r min_sex_ratio_age$age_group` year age group.
The median age of surveyed individuals was `r medage` years (Q1-Q3 of `r iqr`
years). Children under five years of age made up 
`r fmt_count(study_data_cleaned, age_in_years < 5)`of the surveyed individuals.
The highest number of surveyed indivduals (unweighted) were in the 
`r table(study_data_cleaned$age_group) %>% which.max() %>% names()`
year age group.

Unweighted age distribution of population by year age group and gender.

<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// describe_by_age_group_and_sex \\\
--------------------------------------------------------------------------------

This chunk will create an unweighted table of survey individuals by age group 
and sex.

Note that proportions are of the total sample (not within each gender) 
to change this, set proptotal = FALSE
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r describe_by_sex}

tab_linelist(study_data_cleaned, age_group, 
             strata     = sex, 
             row_total  = TRUE,
             prop_total = TRUE) %>%
  ## select and rename column names appropriately
  select("Age"              = "value",
         "Female cases (n)" = "female n",
         "Female %"                = "female proportion",
         "Male cases (n)"   = "male n",
         "Male %"                = "male proportion",
         "Total") %>%
  kable(digits = 1)


```

## Vaccination coverage

Weighted vaccination coverage; accepting equal validity from self-reported and 
card-reported vaccination status

<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// vaccination_coverage_overall \\\
--------------------------------------------------------------------------------

The below chunk creates a weighted table of counts proportions for vaccination 
coverage while accpeting equal validity from self- and card-reporting. 

Note that this includes a design effect. 

Note that low counts or short observation times may lead to a confidence interval 
that crosses zero (i.e. negative) for mortality ratios. These should be interpreted
as if no deaths or recoded to zero (impossible to have negative deaths). 
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r msf_vaccination_coverage}

##JULIA: what's happening - giving way too many children in the results.
survey_design %>%  # use the survey object (weighted)
  ## calculate weighted counts and weighted proportions
  tab_survey(msf_vacc_status, deff = TRUE) %>%
  ## select and rename appropriate columns 
  select("MSF vaccination status" = value, 
         "Children (n)" = n, 
         "% (95% CI)" = ci,
         "Design effect" = deff) %>%
  kable(digits = 1)

survey_design


```



```{r routine_vaccination_coverage}

survey_design %>%  # use the survey object (weighted)
  ## calculate weighted counts and weighted proportions
  tab_survey(routine_vacc_status, deff = TRUE) %>%
  ## select and rename appropriate columns 
  select("Routine vaccination status" = value, 
         "Children (n)" = n, 
         "% (95% CI)" = ci,
         "Design effect" = deff) %>%
  kable(digits = 1)

```



```{r sia_vaccination_coverage}


survey_design %>%  # use the survey object (weighted)
  ## calculate weighted counts and weighted proportions
  tab_survey(sia_vacc_status, deff = TRUE) %>%
  ## select and rename appropriate columns 
  select("SIA vaccination status" = value, 
         "Children (n)" = n, 
         "% (95% CI)" = ci,
         "Design effect" = deff) %>%
  kable(digits = 1)

```



Weighted vaccination coverage; distinguishing between vaccination cards and 
verbal confirmation 

<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// vaccination_coverage_overall_detail \\\
--------------------------------------------------------------------------------

The below chunk creates a weighted table of counts proportions for vaccination 
coverage while distinguishing validity from self- and card-reporting. 

Note that low counts or short observation times may lead to a confidence interval 
that crosses zero (i.e. negative) for mortality ratios. These should be interpreted
as if no deaths or recoded to zero (impossible to have negative deaths). 
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r MSF vacc_coverage_detail}

survey_design %>% # use the survey object (weighted)
  ## calculate weighted counts and weighted proportions
  tab_survey(msf_vacc) %>% 
  select("MSF vaccination status" = value, 
         "Children (n)" = n,  
         "% (95% CI)" = ci) %>% 
  kable(digits = 1)
```



Weighted vaccination coverage by health district; accepting equal validity from
self-reported and card-reported vaccination status 

<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// vaccination_coverage_strata \\\
--------------------------------------------------------------------------------

The below chunk creates a weighted table of counts proportions for vaccination 
coverage while accpeting equal validity from self- and card-reporting, 
stratified by health district. 

Note that this includes a design effect. 

Note that low counts or short observation times may lead to a confidence interval 
that crosses zero (i.e. negative) for mortality ratios. These should be interpreted
as if no deaths or recoded to zero (impossible to have negative deaths). 
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r vaccination_coverage_strata}

survey_design %>%  # use the survey object (weighted)
  tab_survey(vaccination_status_simple, strata = health_district) %>% 
  select(-variable) %>%
  rename("Vaccination status" = value) %>% 
  augment_redundant(" (n)"         = " n") %>%  # wrap all "n" in braces (note space before n)
  rename_redundant("% (95% CI)"    = " ci") %>% # relabel all columns containing "ci"
  kable(digits = 1)
```





Weighted vaccination coverage by sex; accepting equal validity from self-reported 
and card-reported vaccination status

<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// vaccination_coverage_sex \\\
--------------------------------------------------------------------------------

The below chunk creates a weighted table of counts proportions for vaccination 
coverage while accpeting equal validity from self- and card-reporting; broken 
down by sex. 

Note that low counts or short observation times may lead to a confidence interval 
that crosses zero (i.e. negative) for mortality ratios. These should be interpreted
as if no deaths or recoded to zero (impossible to have negative deaths). 
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r vaccination_coverage_sex}

survey_design_ %>% # use the survey object (weighted)
  ## calculate weighted counts and weighted proportions - stratified by sex
  tab_survey(msf_vacc, strata = sex, deff = TRUE) %>%
  select(-variable) %>%
  rename("Vaccination status" = value) %>% 
  augment_redundant(" (n)"         = " n") %>%  # wrap all "n" in braces (note space before n)
  rename_redundant("% (95% CI)"    = " ci",      # relabel all columns containing "ci"
                   "Design Effect" = " deff") %>% # "deff" to "Design effect"
  kable(digits = 1)
```



Weighted vaccination coverage by sex; distinguishing between vaccination cards 
and verbal confirmation

<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// vaccination_coverage_sex_detail \\\
--------------------------------------------------------------------------------

The below chunk creates a weighted table of counts proportions for vaccination 
coverage while distinguishing validity from self- and card-reporting; broken 
down by sex. 

Note that low counts or short observation times may lead to a confidence interval 
that crosses zero (i.e. negative) for mortality ratios. These should be interpreted
as if no deaths or recoded to zero (impossible to have negative deaths). 
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r vaccination_coverage_sex_detail}
# return weighted counts and weighted proportions 
survey_design %>% 
  tab_survey(vaccination_status, strata = sex) %>%
  select(-variable) %>%
  rename("Vaccination status" = value) %>% 
  augment_redundant(" (n)"         = " n") %>%  # wrap all "n" in braces (note space before n)
  rename_redundant("% (95% CI)"    = " ci"      # relabel all columns containing "ci"
                   ) %>% 
  kable(digits = 1)
```



Weighted vaccination coverage by age group; accepting equal validity from self-reported and card-reported vaccination status

<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// vaccination_coverage_age_group \\\
--------------------------------------------------------------------------------

The below chunk creates a weighted table of counts proportions for vaccination 
coverage while accpeting equal validity from self- and card-reporting; broken 
down by age group.  

Note that low counts or short observation times may lead to a confidence interval 
that crosses zero (i.e. negative) for mortality ratios. These should be interpreted
as if no deaths or recoded to zero (impossible to have negative deaths). 
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r vaccination_coverage_age_group}
 
survey_design %>% 
  tab_survey(vaccination_status_simple, strata = age_group, deff = TRUE, 
             digits = 1, drop = "Missing", transpose = "value") %>%
  rename("Age group (years)" = age_group) %>% 
  augment_redundant(" (n)"         = " n") %>%  # wrap all "n" in braces (note space before n)
  rename_redundant("% (95% CI)"    = " ci",       # relabel all columns containing "ci"
                   "Design Effect" = " deff") %>% # "deff" to "Design effect"
  kable(digits = 1)
```



Weighted vaccination coverage by age group; distinguishing between vaccination 
cards and verbal confirmation 

<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// vaccination_coverage_sex_detail \\\
--------------------------------------------------------------------------------

The below chunk creates a weighted table of counts proportions for vaccination 
coverage while distinguishing validity from self- and card-reporting; broken 
down by age group.  

Note that low counts or short observation times may lead to a confidence interval 
that crosses zero (i.e. negative) for mortality ratios. These should be interpreted
as if no deaths or recoded to zero (impossible to have negative deaths). 
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r vaccination_coverage_age_group_detail}
 
survey_design %>% 
  tab_survey(vaccination_status, strata = age_group, 
             drop = "Missing", transpose = "value") %>%
  rename("Age group (years)" = age_group) %>% 
  augment_redundant(" (n)"         = " n") %>%  # wrap all "n" in braces (note space before n)
  rename_redundant("% (95% CI)"    = " ci"      # relabel all columns containing "ci"
                   ) %>%
  kable(digits = 1)
```


## Reasons for not vaccinating 

Weighted counts and proportions for reasons not vaccinated in routine and 
campaign circumstances, individually, among those not vaccinated
<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// no_vacc_reason_routine_campaign_combo \\\
--------------------------------------------------------------------------------

The below chunk creates a weighted table of counts proportions for reasons 
not vaccinated broken down by routine and campaign.  

This happens in three steps: 
- Counts and weighted proportions for routine
- Counts and weighted proportions for campaign 
- bind the columns together 

Note that low counts or short observation times may lead to a confidence interval 
that crosses zero (i.e. negative) for mortality ratios. These should be interpreted
as if no deaths or recoded to zero (impossible to have negative deaths). 
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r no_vacc_reason_routine_campaign_combo}

## routine reasons 
routine <- survey_design %>% 
  ## filter for those not vaccinated 
  filter(str_detect(vaccine_routine, pattern = fixed("Yes -"), negate = TRUE)) %>%
  tab_survey(q7_no_routine_vacc_r) %>%
  # rename columns appropriately
  select("Reasons" = value, 
         "Routine (n)" = n , 
         "% (95% CI)" = ci)

## campaign reasons 
campaign <- survey_design %>% 
  ## filter for not vaccinated 
  filter(str_detect(vaccine_mass, pattern = fixed("Yes -"), negate = TRUE)) %>%
  tab_survey(q28_no_campaign_vacc_r) %>% 
  ## rename remaining columns appropriately 
  select("Campaign (n)" = n, 
         "% (95% CI)" = ci)
  
## bind two together 
bind_cols(routine, 
          campaign) %>% 
  kable(digits = 1)

```


Weighted counts and proportions for reasons not vaccinated in supplemented 
immunisation activities, among those not vaccinated

<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// no_vacc_reason_sia \\\
--------------------------------------------------------------------------------

The below chunk creates a weighted table of counts proportions for reasons 
not vaccinated during supplemented immunisation activitites. 

Note that low counts or short observation times may lead to a confidence interval 
that crosses zero (i.e. negative) for mortality ratios. These should be interpreted
as if no deaths or recoded to zero (impossible to have negative deaths). 
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->
```{r no_vacc_reason_sia}

survey_design %>% 
  filter(str_detect(vaccine_sia, pattern = fixed("Yes -"), negate = TRUE)) %>%
  tab_survey(q38_no_sia_vacc_reason) %>%
  ## rename columns appropriately
  select("Reasons" = value, 
         "Routine (n)" = n , 
         "% (95% CI)" = ci) %>%
  kable(digits = 1)
```

