---
title: "Beboto vaccination coverage survey"
output: 
  word_document:
    keep_md: true
---


# Introduction to this template

- For a more detailed explanation of this template, please visit https://r4epis.netlify.com/surveys  

- Text within <! > will not show in your final document. These comments are used
to explain the template. You can delete them if you want.

## Installing and loading required packages 

<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// setup \\\
-------------------------------------------------------------------------------->
  

```{r setup, include = FALSE, results='hide', message=FALSE, warning=FALSE}
## hide all code chunks in the output, but show errors
knitr::opts_chunk$set(echo = FALSE, error = TRUE, fig.width = 6*1.25, fig.height = 6)


## set default NA to - in output, define figure width/height
options(knitr.kable.NA = "-")


## Installing required packages for this template
required_packages <- c("knitr",       # create output docs
                       "here",        # find your files
                       "rio",         # for importing data
                       "epitrix",     # clean/shape data
                       "dplyr",       # clean/shape data
                       "tidyr",       # clean/shape data
                       "forcats",     # manipulate and rearrange factors
                       "stringr",     # manipulate texts
                       "ggplot2",     # create plots and charts
                       "sitrep",      # MSF field epi functions
                       "survey",      # for survey functions
                       "srvyr"        # dplyr wrapper for survey package
                       )

for (pkg in required_packages) {
  ## install packages if not already present
  if (!pkg %in% rownames(installed.packages())) {
    install.packages(pkg)
  }
  
  ## load packages to this current session 
  library(pkg, character.only = TRUE)
}


## set default text size to 18 for plots
## give classic black/white axes for plots
ggplot2::theme_set(theme_classic(base_size = 18))


```

<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
You should load your data as a linelist, where each row is one person. 

Generally, survey datasets will have two levels:
One for household and one for individual (to combine see merge_data_levels).
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// read_nonDHARMA_data \\\
--------------------------------------------------------------------------------
This section is for data not from Dharma. 
If you have already loaded data from Dharma, go to merge_data_levels
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r read_nonDHIS_data, warning = FALSE, message = FALSE}

## Excel file ------------------------------------------------------------------

## read in household data sheet
study_data_hh <- rio::import(here::here("7.analysis", "data", "vaccination_coverage_cleaned.xlsx"), 
                             which = "hh level", na = ".")

## read in individual level data sheet
study_data_indiv <- rio::import(here::here("7.analysis", "data", "vaccination_coverage_cleaned.xlsx"), 
                                which = "ind level", na = ".")

```



<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// merge_data_levels \\\
--------------------------------------------------------------------------------
For survey datasets with two levels (e.g. household and individual), 
these levels will need to be merged in to one dataset. 

This is done using a unique identifier for the household 
(which has to be repeated for each row in the individuals dataset) 
For a Dharma dataset this variable is "fact_0_id".
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r merge_data_levels}

## make sure each individual has the ID 
## (equivalent of excel drag downwards to fill blanks)
#study_data_indiv <- study_data_indiv %>% fill(merge_id)

## join the individual and household data to form a complete data set
study_data_raw <- left_join(study_data_hh, study_data_indiv, by = "merge_id")


```



<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// prep_DHARMA_data \\\
--------------------------------------------------------------------------------
This section is to import your data dictionary and standardise variable names. 

The Dharma data dictionary has variable names
in the column_name column. Possible values for each variable are
specified in choice_code and choice_name columns. 
Code has the shortened value and Name has the full-text value.
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r prep_data}

## make a copy of your orginal dataset and name it study_data_cleaned
study_data_cleaned <- study_data_raw

```



<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// read_population_data \\\
--------------------------------------------------------------------------------
This template uses population data to create survey weights. 

There are three options:
- You can read in a spreadsheet with age group, sex and region data.
- You can put in the specific populations into the gen_population function. 
- If you have the total or regional populations, you can estimate the age group
from proportions.

Below we show basic examples for reading data and entering counts - as well as 
a more complex version using proportions to get the age/sex breakdown in 
two seperate regions. (Useful if doing a stratified survey)


Age group proportions are from the OCBA population denominators tool v1. The
proportions below are for sub-Saharan Africa in 2019. They are only an estimate!
If you have more specific proportions, you can use them below.
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r read_population_data, warning = FALSE, message = FALSE}


## Read data -------------------------------------------------------------------

## This step reads in your population data from Excel.
## You may need to rename your columns.

# population_data <- rio::import(here::here("population.xlsx"), which = "Sheet1")

## repeat preparation steps as appropriate


## Enter counts directly -------------------------------------------------------


#Enter population counts by groups. 

population_6m9y <- gen_population(
  groups = c("6 months-9 years"), 
  counts = c(24711), 
  strata = NULL) %>%
  rename (age_group = groups, 
          population = n)


## Create counts from proportions ----------------------------------------------
## This step helps you estimate sub-group size with proportions.
## You need to replace the total_pop and proportions. You can change the groups
## to fit your needs. 

## Here we repeat the steps for two regions (district A and B) then bind the two
## together 


## generate population data by age groups in years for district A
#population_data_age_district_a <- gen_population(total_pop = 10000, # set total population 
#  groups      = c("0", "1", "2", "3", "4", "5+"), # set groups
#  proportions = c(0.0164, 0.0164, 0.015, 0.015,
#                  0.015, 0.1386), # set proportions for each group
#  strata      = c("Male", "Female")) %>%           # stratify by gender
#  rename(age_group  = groups,                      # rename columns (NEW NAME = OLD NAME)
#         sex        = strata,
#         population = n) %>% 
#  mutate(health_district = "District A")           # add a column to identify region 


## generate population data by age groups in years for district B
#population_data_age_district_b <- gen_population(total_pop = 10000, # set total population 
#  groups      = c("0", "1", "2", "3", "4", "5+"), # set groups
#  proportions = c(0.0164, 0.0164, 0.015, 0.015,
#                  0.015, 0.1386), # set proportions for each group
#  strata      = c("Male", "Female")) %>%           # stratify by gender
#  rename(age_group  = groups,                      # rename columns (NEW NAME = OLD NAME)
#         sex        = strata,
#         population = n) %>% 
#  mutate(health_district = "District B")           # add a column to identify region 



## bind region population data together to get overall population 
#population_data_age <- bind_rows(population_data_age_district_a, 
#                                 population_data_age_district_b)
```


<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// cluster_counts \\\
--------------------------------------------------------------------------------
For cluster surveys you may want to add survey weights at the cluster level. 

This could be done as in the read_population_data chunk. 

Alternatively if there are only a few counts, these could be entered as below
in to a tibble. 

In any case you will need to have one column with a cluster identifier which 
matches your survey data, and another column with the number of households in 
each cluster. 

~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r cluster_counts}

#read data in
cluster_counts <- rio::import(here::here("7.analysis","data", "cluster counts.xlsx"))

#round digits
cluster_counts$total_hh <- round(cluster_counts$total_hh, digits = 0)

#drop population column
cluster_counts <- cluster_counts %>%
    select(-pop)

#might need to be a tibble for code later? the template had this created as a tibble but I imported instead. 
as_tibble(cluster_counts)


```




<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// browse_data \\\
--------------------------------------------------------------------------------

You'll want to look at your data. Here are a few ways you can explore.
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r browse_data, eval = FALSE}

##Julia note: this is weird, it's returning ages that are less than (e.g. age of routine vaccination is 11 months and current age is 9 months. that's normal...)

## check for logical date inconsistencies 
## for example check vaccination age greater than current age and return corresponding IDs
study_data_raw %>% 
  filter(age_routine_vacc > age_months) %>% 
  select(merge_id, age_routine_vacc,age_months)

```

<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// standardise_dates \\\
--------------------------------------------------------------------------------
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->




```{r standardise_dates}

## use the guess_dates() function to make a first pass at date variables.
study_data_cleaned <- study_data_cleaned %>%
   mutate_at(vars(matches("date|Date")), linelist::guess_dates,
             error_tolerance = 0.5)

#checked class of "today" date variable - it's character. 
class(study_data_cleaned$today)

#change "today" date variable to a date:
study_data_cleaned$today <- as.Date(study_data_cleaned$today, format = "%Y-%m-%d")

#drop data from training and pilot day
table(study_data_cleaned$today) # check which dates need to be dropped
#drop dates older than April 1, 2020
study_data_cleaned <- subset(study_data_cleaned, today >= "2020-04-01")


```


```{r cleaning}

#checked in excel to find weirdness for variables, like we did each day during survey. Corrected hh number, cluster number, and team number for some. 

#checking for weirdness here & corrected in excel if necessary
#any houshold marked as both first AND second visit on the same line. 
#table(study_data_cleaned$first_visit, study_data_cleaned$second_visit)
#any empty hh that gave consent
#table(study_data_cleaned$empty_household, study_data_cleaned$consent)

#changed character variables that I'll be using to numeric: 
study_data_cleaned$children_count <- as.numeric(study_data_cleaned$children_count)
study_data_cleaned$cluster_number <- as.numeric(study_data_cleaned$cluster_number)
study_data_cleaned$household_number <- as.numeric(study_data_cleaned$household_number)



```

<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// factor_vars \\\
--------------------------------------------------------------------------------

This chunk will help you clean factor variables.
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r factor_vars}

##JULIA - ignoring for now, will return if I really need true/false. for now variables are well named, and we'll see what the need is for true/false later. 

## Change a yes/no variable in to TRUE/FALSE
## create a new variable called consent 
## where the old one is yes place TRUE in the new one
#study_data_cleaned <- study_data_cleaned %>% 
#  mutate(consent = q58_consent == "Yes")


#JULIA ignored code below because had only one case of no consent. (found by: table(study_data_cleaned$no_consent_reason)

## create a new variable by reordering the levels of a factor 
#study_data_cleaned <- study_data_cleaned %>%
#  mutate(no_consent = fct_relevel(q65_consent_no_reason,
#                                  "Refuse to explain", 
#                                  "No time", 
#                                  "Bad experience",
#                                  "Other reason")
#        )


## combine all vaccine variables in to one 
## keep the yes answers and change others to no 
## if missing in all three vars then stays NA

##JULIA - I stopped doing this for now - wasn't sure it was needed yet. Code definitely needs adapting to this data - as is I created a variable that says 100% unvaccinated. Will come back to this if needed. 

#study_data_cleaned <- study_data_cleaned %>% 
#  mutate(vaccination_status = case_when(
#    is.na(msf_vacc) & 
#      is.na(routine_vacc) & 
#      is.na(sia_vacc)  ~ NA_character_,
#    msf_vacc    == "Yes - Vaccination card" ~ "Card", 
#    routine_vacc == "Yes - Vaccination card" ~ "Card", 
#    sia_vacc     == "Yes - Vaccination card" ~ "Card", 
#    msf_vacc    == "Yes - Verbal"           ~ "Verbal", 
#    routine_vacc == "Yes - Verbal"           ~ "Verbal", 
#    sia_vacc     == "Yes - Verbal"           ~ "Verbal", 
#    TRUE                                        ~ "Unvaccinated")
#    )

#checking the variable we created above. 
#table(study_data_cleaned$msf_vacc)



## correct the order of levels in newly created var
#study_data_cleaned <- study_data_cleaned %>% 
#  mutate(vaccination_status = fct_relevel(vaccination_status, 
#                                          "Card", 
#                                          "Verbal", 
#                                          "Unvaccinated")
#  )


## create a new grouping for vaccine status variable 
## simplified, card or verbal then yes otherwise no . 

#JULIA same problem as above - needs work if i want to use this. 
#study_data_cleaned <- study_data_cleaned %>% 
#  mutate(
#    vaccination_status_simple = case_when(
#      is.na(vaccination_status)                   ~ NA_character_,
#      vaccination_status %in% c("Card", "Verbal") ~ "Vaccinated", 
#      TRUE                                        ~ "Unvaccinated")
#    )


## correct the order of levels in newly created var
#study_data_cleaned <- study_data_cleaned %>% 
#  mutate(vaccination_status_simple = fct_relevel(vaccination_status_simple, 
#                                                 "Vaccinated", 
#                                                 "Unvaccinated")
#  )

## explicitly replace NA of a factor
#study_data_cleaned <- study_data_cleaned %>%
#  mutate(vaccine_routine = fct_explicit_na(vaccine_routine, na_level = "No answer"))

```





<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// remove_unused_data \\\
--------------------------------------------------------------------------------

Your data might have empty rows or columns you want to remove.
You can also use this section to create temporary datasets so you can review
specific variables or rows.

You may want to drop rows with missing IDs (i.e. blank rows from excel) 

Those without consent need to be dropped too

It is important that you drop observations before adding survey weights!
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r remove_unused_data}
## Drop unused rows  -----------------------------------------------------------

## store the cases that you drop so you can describe them (e.g. non-consenting)
dropped <- study_data_cleaned %>% 
  filter(consent == "no")

## drop the unused rows from the survey data set  
study_data_cleaned <- study_data_cleaned %>%
  filter(consent == "yes")


## Drop columns ----------------------------------------------------------------
## OPTIONAL: This step shows you how you can remove certain variables.
## study_data_cleaned <- select(study_data_cleaned, -c("age_years", "sex"))

## OPTIONAL: if you want to inspect certain variables, you can select these by
## name or column number. This example creates a reduced dataset for the first
## three columns, age_years, and sex.

# study_data_reduced <- select(study_data_cleaned, c(1:3, "age_years", "sex")
```


<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// survey_weights \\\
--------------------------------------------------------------------------------

Create survey weights according to your study design. 

These require information on the source population and/or the clusters surveyed. 

There are three options, comment out those you do not use: 
- Stratified 
- Cluster 
- Stratified and cluster 

~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r survey_weights}

## stratified ------------------------------------------------------------------

## create a variable called "surv_weight_strata" 
## contains weights for each individual - by age group, sex and health district
#study_data_cleaned <- add_weights_strata(x = study_data_cleaned, 
#                                         p = population_data_age, 
#                                         surv_weight = "surv_weight_strata",
#                                         surv_weight_ID = "surv_weight_ID_strata",
#                                         age_group, sex, health_district)


## cluster ---------------------------------------------------------------------

## merge village and household to create a unique household ID 
study_data_cleaned <- study_data_cleaned %>% 
  mutate(hh_id = str_glue("{village_name}_{household_number}"))


## create cluster weights 
#https://rdrr.io/github/R4EPI/sitrep/man/add_weights_cluster.html

study_data_cleaned <- add_weights_cluster(x = study_data_cleaned, 
                                          cl = cluster_counts, 
                                          eligible = children_count, 
                                          interviewed = children_count, 
                                          cluster_x = village_name, 
                                          cluster_cl = village_name, 
                                          household_x = household_number, 
                                          household_cl = total_hh, 
                                          surv_weight = "surv_weight_cluster", 
                                          surv_weight_ID = "surv_weight_ID_cluster", 
                                          ignore_cluster = FALSE, 
                                          ignore_household = FALSE)

## stratified and cluster ------------------------------------------------------

# ## create a survey weight for cluster and strata 
# study_data_cleaned <- study_data_cleaned %>% 
#   mutate(surv_weight_cluster_strata = surv_weight_strata * surv_weight_cluster)


```



<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// survey_design \\\
--------------------------------------------------------------------------------

Create survey object according to your study design. 

Used the same way as dataframes to calculate weight proportions etc. 

Make sure that all necessary variables are created before this. 

There are four options, comment out those you do not use: 
- Simple random 
- Stratified 
- Cluster 
- Stratified cluster

For this template - we will pretend that we cluster surveys in two seperate 
strata (health districts A and B). 
So to get overall estimates we need have combined cluster and strata weights. 
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r survey_design}

## simple random ---------------------------------------------------------------

survey_design_simple <- study_data_cleaned %>% 
  as_survey_design(ids = 1, # 1 for no cluster ids 
                   weights = NULL, # No weight added
                   strata = NULL # sampling was simple (no strata)
                  )

## stratified ------------------------------------------------------------------

survey_design_strata <- study_data_cleaned %>% 
  as_survey_design(ids = 1, # 1 for no cluster ids 
                   weights = surv_weight_strata, # weight variable created above 
                   strata = health_district # sampling was stratified by district
                  )

## cluster ---------------------------------------------------------------------

survey_design_cluster <- study_data_cleaned %>% 
  as_survey_design(ids = village, # 1 for no cluster ids 
                   weights = surv_weight_cluster, # weight variable created above 
                   strata = NULL # sampling was simple (no strata)
                  )

## stratified cluster ----------------------------------------------------------

survey_design <- study_data_cleaned %>% 
  as_survey_design(ids = village, # 1 for no cluster ids 
                   weights = surv_weight_cluster_strata, # weight variable created above 
                   strata = health_district # sampling was simple (no strata)
                  )
```



<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// save_cleaned_data \\\
--------------------------------------------------------------------------------

You can save your cleaned dataset as an Excel. 
This automatically names your file "study_data_cleaned_DATE", where DATE is the
current date.
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r save_cleaned_data}
# rio::export(study_data_cleaned, str_glue("study_data_cleaned_{Sys.Date()}.xlsx"))
```



# Results

## Survey inclusion 


<!--~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// inclusion_counts \\\
--------------------------------------------------------------------------------

The below chunks calculate values that are displayed with the inline text

Get the counts of clusters and households included 
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~-->

```{r inclusion_counts}

## get counts of number of clusters 
num_clus <- study_data_cleaned %>%
  ## trim data to unique clusters
  distinct(cluster_number) %>% 
  ## get number of rows (count how many unique)
  nrow()

## get counts of number households 
num_hh <- study_data_cleaned %>% 
  ## get unique houses by cluster
  distinct(cluster_number, q14_hh_no) %>% 
  ## get number of rounds (count how many unique)
  nrow()

```


We included `r num_hh` households accross `r num_clus` clusters in this survey analysis. 


Among the `r nrow(dropped)` individuals without consent to participate in the survey, 
the reasons for refusal are described below. 

<!--~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// consent_reasons \\\
--------------------------------------------------------------------------------

This chunk will create a table of dropped individuals by reason for no consent. 

Note that these reasons are spread over multiple columns, thus the proportion
needs to be of the total and missings need to be dropped. 
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~-->

```{r consent_reasons}

## using the dataset with dropped individuals 
tab_linelist(dropped, "q65_consent_no_reason", col_total = TRUE, digits = 1) %>% 
  ## drop variable column and rename others
  select("Reason" = value, 
         "n" = n, 
         "%" = proportion) %>%
  kable(digits = 1)
```



<!--~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// cluster_hh_size \\\
--------------------------------------------------------------------------------

The below chunks calculate values that are displayed with the inline text

Get counts of households per cluster and individuals per household. 
From these create medians and standard deviations. 
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~-->

```{r cluster_hh_size}

## get counts of the number of households per cluster
clustersize <- study_data_cleaned %>% 
  ## trim data to only unique households within each cluster
  distinct(cluster_number, q14_hh_no) %>%
  ## count the number of households within each cluster
  count(cluster_number) %>% 
  pull(n)

## get the median number of households per cluster
clustermed <- median(clustersize)

## get the min and max number of households per cluster
## paste these together seperated by a dash 
clusterrange <- str_c(range(clustersize), collapse = "--")

## get counts of children per household 
## do this by cluster as household IDs are only unique within clusters
hhsize <- study_data_cleaned %>% 
  count(cluster_number, q14_hh_no) %>%
  pull(n) 

## get median number of children per household
hhmed <- median(hhsize)
## get the min and max number of children per household
## paste these together seperated by a dash 
hhrange <- str_c(range(hhsize), collapse = "--")

# get standard deviation 
hhsd <- round(sd(hhsize), digits = 1)
```


The median number of households per cluster was
`r clustermed`, with a range of `r clusterrange`. The median number of children
per household was `r hhmed` (range: `r hhrange`, standard deviation: `r hhsd`). 


## Demographic information


In total we included `r nrow(study_data_cleaned)` in the survey analysis. 
The age break down and a comparison with the source population is shown below. 


<!--~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// descriptive_sampling_bias \\\
--------------------------------------------------------------------------------

Compare the proportions in each age group between your sample and 
the source population. 

This is important to be able to highlight potential sampling bias. 
You could similarly repeat this looking at distributions by sex. 

Note that these p-values are just indicative, and a descriptive discussion (or
visualisation with age-pyramids below) of the distributions in your study sample 
compared to the source population is more
important that the binomial test itself. This is because increasing sample size
will more often than not lead to differences that may be irrelevant after weighting
your data. 

~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~-->

```{r descriptive_sampling_bias, warning = FALSE}
## counts and props of the study population
ag <- tab_linelist(study_data_cleaned, "age_group") %>%
  mutate(n_total = sum(n)) %>%
  select(-variable) %>%
  rename(age_group = value) %>%
  mutate(age_group = fct_inorder(age_group))

## counts and props of the source population
propcount <- group_by(population_data_age, age_group) %>%
    tally(population) %>%
    mutate(proportion = n / sum(n))

## bind together the columns of two tables, group by age, and perform a 
## binomial test to see if n/total is significantly different from population
## proportion.
  ## suffix here adds to text to the end of columns in each of the two datasets
left_join(ag, propcount, by = "age_group", suffix = c("", "_pop")) %>%
  group_by(age_group) %>%

  ## broom::tidy(binom.test()) makes a data frame out of the binomial test and
  ## will add the variables p.value, parameter, conf.low, conf.high, method, and
  ## alternative. We will only use p.value here. You can include other
  ## columns if you want to report confidence intervals
  mutate(binom = list(broom::tidy(binom.test(n, n_total, proportion_pop)))) %>%
  unnest(cols = c(binom)) %>% # important for expanding the binom.test data frame
  mutate(proportion_pop = proportion_pop * 100) %>%

  ## Adjusting the p-values to correct for false positives 
  ## (because testing multiple age groups). This will only make 
  ## a difference if you have many age categories
  mutate(p.value = p.adjust(p.value, method = "holm")) %>%
  select(age_group, n, proportion, n_pop, proportion_pop, p.value) %>%
                      
  ## Only show p-values over 0.001 (those under report as <0.001)
  mutate(p.value = ifelse(p.value < 0.001, "<0.001", as.character(round(p.value, 3)))) %>%

  ## rename the columns appropriatley
  rename(
    "Age group" = age_group,
    "Study population (n)" = n,
    "%" = proportion,
    "Source population (n)" = n_pop,
    "%" = proportion_pop,
    "P-value" = p.value
  ) %>%
  kable(digits = 1)

```



<!--~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// median_age_sex_ratios \\\
--------------------------------------------------------------------------------

The below chunk calculate values that are displayed inline

This returns the median age and sex ratios overall as well as by age group. 
It also pulls the age group with the highest sex ratio. 

~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~-->

```{r median_age_sex_ratios}
## compute the median age 
medage <- median(study_data_cleaned$age_in_years)
## paste the lower and uper quartile together
iqr <- str_c(  # basically copy paste togehter the following
  ## calculate the 25% and 75% of distribution, with missings removed
  quantile(     
    study_data_cleaned$age_in_years, 
    c(0.25, 0.75), 
    na.rm = TRUE), 
  ## between lower and upper place an en-dash
  collapse = "--")


## compute overall sex ratio 
sex_ratio <- study_data_cleaned %>% 
  count(sex) %>% 
  pivot_wider(names_from = sex, values_from = n) %>% 
  mutate(ratio = round(Male/Female, digits = 3)) %>%
  pull(ratio)

## compute sex ratios by age group 
sex_ratio_age <- study_data_cleaned %>% 
  count(age_group, sex) %>% 
  pivot_wider(names_from = sex, values_from = n) %>% 
  mutate(ratio = round(Male/Female, digits = 3)) %>%
  select(age_group, ratio)

## sort table by ascending ratio then select the lowest (first)
min_sex_ratio_age <- arrange(sex_ratio_age, ratio) %>% slice(1)
```

Among the `r nrow(study_data_cleaned)` surveyed individuals, there were 
`r fmt_count(study_data_cleaned, sex == "Female")` females and 
`r fmt_count(study_data_cleaned, sex == "Male")` males (unweighted). The male to
female ratio was `r sex_ratio` in the surveyed population. The lowest male to
female ratio was `r min_sex_ratio_age$ratio`
in the `r min_sex_ratio_age$age_group` year age group.
The median age of surveyed individuals was `r medage` years (Q1-Q3 of `r iqr`
years). Children under five years of age made up 
`r fmt_count(study_data_cleaned, age_in_years < 5)`of the surveyed individuals.
The highest number of surveyed indivduals (unweighted) were in the 
`r table(study_data_cleaned$age_group) %>% which.max() %>% names()`
year age group.

Unweighted age distribution of population by year age group and gender.

<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// describe_by_age_group_and_sex \\\
--------------------------------------------------------------------------------

This chunk will create an unweighted table of survey individuals by age group 
and sex.

Note that proportions are of the total sample (not within each gender) 
to change this, set proptotal = FALSE
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r describe_by_age_group_and_sex}

tab_linelist(study_data_cleaned, age_group, 
             strata     = sex, 
             row_total  = TRUE,
             col_total  = TRUE,
             prop_total = TRUE) %>%
  ## select and rename column names appropriately
  select("Age"              = "value",
         "Female cases (n)" = "Female n",
         "%"                = "Female proportion",
         "Male cases (n)"   = "Male n",
         "%"                = "Male proportion",
         "Total") %>%
  kable(digits = 1)
```



Unweighted age distribution of population by age category (month and year) and gender.

<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// describe_by_age_category_and_sex \\\
--------------------------------------------------------------------------------

This chunk will create an unweighted table of survey individuals by age category 
and sex (i.e. a breakdown by months and years combined).

Note that proportions are of the total sample (not within each gender) 
to change this, set proptotal = FALSE
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r describe_by_age_category_and_sex}

tab_linelist(study_data_cleaned, age_category, 
             strata     = sex, 
             row_total  = TRUE,
             col_total  = TRUE,
             prop_total = TRUE) %>%
  ## select and rename column names appropriately
  select("Age"              = "value",
         "Female cases (n)" = "Female n",
         "%"                = "Female proportion",
         "Male cases (n)"   = "Male n",
         "%"                = "Male proportion",
         "Total") %>%
  kable(digits = 1)
```


There were `r fmt_count(study_data_cleaned, is.na(sex))` cases missing information on sex and 
`r fmt_count(study_data_cleaned, is.na(age_group))` missing age group.

Unweighted age and gender distribution of household population covered by the survey.
<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// age_pyramid \\\
--------------------------------------------------------------------------------

This chunk creates an unweighted (using study_data_cleaned) age/sex pyramid
of your cases.
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r age_pyramid, warning=FALSE}

plot_age_pyramid(study_data_cleaned, 
                 age_group = "age_group", 
                 split_by = "sex",
                 proportion = TRUE) + 
  labs(y = "Proportion", x = "Age group (years)") + # change axis labels
  theme(legend.position = "bottom",     # move legend to bottom
        legend.title = element_blank(), # remove title
        text = element_text(size = 18)  # change text size
       )
```


Unweighted age and gender distribution, stratified by health district,
of household population covered by the survey.
<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// age_pyramid_strata \\\
--------------------------------------------------------------------------------

This chunk creates an unweighted (using study_data_cleaned) age/sex pyramid
of your cases, stratified by health district. 

If you have a stratified survey design this may be useful for visualising 
if you have an excess of representation in 
either sex or gender in any of your survey strata. 
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r age_pyramid_strata, warning=FALSE}

plot_age_pyramid(study_data_cleaned, 
                 age_group = "age_group", 
                 split_by = "sex",
                 stack_by = "health_district",
                 proportion = TRUE) + 
  labs(y = "Proportion", x = "Age group (years)") +                 # change axis labels
  theme(legend.position = "bottom",     # move legend to bottom
        legend.title = element_blank(), # remove title
        text = element_text(size = 18)  # change text size
       )
```


Weighted age and gender distribution of household population covered by the survey.  

<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// age_pyramid_survey \\\
--------------------------------------------------------------------------------

This chunk creates a weighted (using survey_design) age/sex pyramid
of your cases.

Note - if this is substantially different to your unweighted 
pyramid, then it may suggest some sampling bias (similarly to the table comparing 
sample and source population distributions by binomial test). 
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r age_pyramid_survey, warning=FALSE}

plot_age_pyramid(survey_design,
                 age_group = "age_group",
                 split_by = "sex", 
                 proportion = TRUE) +
  labs(y = "Proportion", x = "Age group (years)") +                 # change axis labels
  theme(legend.position = "bottom",     # move legend to bottom
        legend.title = element_blank(), # remove title
        text = element_text(size = 18)  # change text size
       )
```



## Vaccination coverage

Weighted vaccination coverage; accepting equal validity from self-reported and 
card-reported vaccination status

<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// vaccination_coverage_overall \\\
--------------------------------------------------------------------------------

The below chunk creates a weighted table of counts proportions for vaccination 
coverage while accpeting equal validity from self- and card-reporting. 

Note that this includes a design effect. 

Note that low counts or short observation times may lead to a confidence interval 
that crosses zero (i.e. negative) for mortality ratios. These should be interpreted
as if no deaths or recoded to zero (impossible to have negative deaths). 
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r vaccination_coverage_overall}

survey_design %>%  # use the survey object (weighted)
  ## calculate weighted counts and weighted proportions
  tab_survey(vaccination_status_simple, deff = TRUE) %>% 
  ## select and rename appropriate columns 
  select("Vaccination status" = value, 
         "Children (n)" = n, 
         "% (95% CI)" = ci,
         "Design effect" = deff) %>% 
  kable(digits = 1)
```


Weighted vaccination coverage; distinguishing between vaccination cards and 
verbal confirmation 

<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// vaccination_coverage_overall_detail \\\
--------------------------------------------------------------------------------

The below chunk creates a weighted table of counts proportions for vaccination 
coverage while distinguishing validity from self- and card-reporting. 

Note that low counts or short observation times may lead to a confidence interval 
that crosses zero (i.e. negative) for mortality ratios. These should be interpreted
as if no deaths or recoded to zero (impossible to have negative deaths). 
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r vaccination_coverage_overall_detail}

survey_design %>% # use the survey object (weighted)
  ## calculate weighted counts and weighted proportions
  tab_survey(vaccination_status) %>% 
  select("Vaccination status" = value, 
         "Children (n)" = n,  
         "% (95% CI)" = ci) %>% 
  kable(digits = 1)
```



Weighted vaccination coverage by health district; accepting equal validity from
self-reported and card-reported vaccination status 

<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// vaccination_coverage_strata \\\
--------------------------------------------------------------------------------

The below chunk creates a weighted table of counts proportions for vaccination 
coverage while accpeting equal validity from self- and card-reporting, 
stratified by health district. 

Note that this includes a design effect. 

Note that low counts or short observation times may lead to a confidence interval 
that crosses zero (i.e. negative) for mortality ratios. These should be interpreted
as if no deaths or recoded to zero (impossible to have negative deaths). 
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r vaccination_coverage_strata}

survey_design %>%  # use the survey object (weighted)
  tab_survey(vaccination_status_simple, strata = health_district) %>% 
  select(-variable) %>%
  rename("Vaccination status" = value) %>% 
  augment_redundant(" (n)"         = " n") %>%  # wrap all "n" in braces (note space before n)
  rename_redundant("% (95% CI)"    = " ci") %>% # relabel all columns containing "ci"
  kable(digits = 1)
```





Weighted vaccination coverage by sex; accepting equal validity from self-reported 
and card-reported vaccination status

<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// vaccination_coverage_sex \\\
--------------------------------------------------------------------------------

The below chunk creates a weighted table of counts proportions for vaccination 
coverage while accpeting equal validity from self- and card-reporting; broken 
down by sex. 

Note that low counts or short observation times may lead to a confidence interval 
that crosses zero (i.e. negative) for mortality ratios. These should be interpreted
as if no deaths or recoded to zero (impossible to have negative deaths). 
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r vaccination_coverage_sex}

survey_design %>% # use the survey object (weighted)
  ## calculate weighted counts and weighted proportions - stratified by sex
  tab_survey(vaccination_status_simple, strata = sex, deff = TRUE) %>%
  select(-variable) %>%
  rename("Vaccination status" = value) %>% 
  augment_redundant(" (n)"         = " n") %>%  # wrap all "n" in braces (note space before n)
  rename_redundant("% (95% CI)"    = " ci",      # relabel all columns containing "ci"
                   "Design Effect" = " deff") %>% # "deff" to "Design effect"
  kable(digits = 1)
```



Weighted vaccination coverage by sex; distinguishing between vaccination cards 
and verbal confirmation

<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// vaccination_coverage_sex_detail \\\
--------------------------------------------------------------------------------

The below chunk creates a weighted table of counts proportions for vaccination 
coverage while distinguishing validity from self- and card-reporting; broken 
down by sex. 

Note that low counts or short observation times may lead to a confidence interval 
that crosses zero (i.e. negative) for mortality ratios. These should be interpreted
as if no deaths or recoded to zero (impossible to have negative deaths). 
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r vaccination_coverage_sex_detail}
# return weighted counts and weighted proportions 
survey_design %>% 
  tab_survey(vaccination_status, strata = sex) %>%
  select(-variable) %>%
  rename("Vaccination status" = value) %>% 
  augment_redundant(" (n)"         = " n") %>%  # wrap all "n" in braces (note space before n)
  rename_redundant("% (95% CI)"    = " ci"      # relabel all columns containing "ci"
                   ) %>% 
  kable(digits = 1)
```



Weighted vaccination coverage by age group; accepting equal validity from self-reported and card-reported vaccination status

<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// vaccination_coverage_age_group \\\
--------------------------------------------------------------------------------

The below chunk creates a weighted table of counts proportions for vaccination 
coverage while accpeting equal validity from self- and card-reporting; broken 
down by age group.  

Note that low counts or short observation times may lead to a confidence interval 
that crosses zero (i.e. negative) for mortality ratios. These should be interpreted
as if no deaths or recoded to zero (impossible to have negative deaths). 
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r vaccination_coverage_age_group}
 
survey_design %>% 
  tab_survey(vaccination_status_simple, strata = age_group, deff = TRUE, 
             digits = 1, drop = "Missing", transpose = "value") %>%
  rename("Age group (years)" = age_group) %>% 
  augment_redundant(" (n)"         = " n") %>%  # wrap all "n" in braces (note space before n)
  rename_redundant("% (95% CI)"    = " ci",       # relabel all columns containing "ci"
                   "Design Effect" = " deff") %>% # "deff" to "Design effect"
  kable(digits = 1)
```



Weighted vaccination coverage by age group; distinguishing between vaccination 
cards and verbal confirmation 

<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// vaccination_coverage_sex_detail \\\
--------------------------------------------------------------------------------

The below chunk creates a weighted table of counts proportions for vaccination 
coverage while distinguishing validity from self- and card-reporting; broken 
down by age group.  

Note that low counts or short observation times may lead to a confidence interval 
that crosses zero (i.e. negative) for mortality ratios. These should be interpreted
as if no deaths or recoded to zero (impossible to have negative deaths). 
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r vaccination_coverage_age_group_detail}
 
survey_design %>% 
  tab_survey(vaccination_status, strata = age_group, 
             drop = "Missing", transpose = "value") %>%
  rename("Age group (years)" = age_group) %>% 
  augment_redundant(" (n)"         = " n") %>%  # wrap all "n" in braces (note space before n)
  rename_redundant("% (95% CI)"    = " ci"      # relabel all columns containing "ci"
                   ) %>%
  kable(digits = 1)
```


## Reasons for not vaccinating 

Weighted counts and proportions for reasons not vaccinated in routine and 
campaign circumstances, individually, among those not vaccinated
<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// no_vacc_reason_routine_campaign_combo \\\
--------------------------------------------------------------------------------

The below chunk creates a weighted table of counts proportions for reasons 
not vaccinated broken down by routine and campaign.  

This happens in three steps: 
- Counts and weighted proportions for routine
- Counts and weighted proportions for campaign 
- bind the columns together 

Note that low counts or short observation times may lead to a confidence interval 
that crosses zero (i.e. negative) for mortality ratios. These should be interpreted
as if no deaths or recoded to zero (impossible to have negative deaths). 
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r no_vacc_reason_routine_campaign_combo}

## routine reasons 
routine <- survey_design %>% 
  ## filter for those not vaccinated 
  filter(str_detect(vaccine_routine, pattern = fixed("Yes -"), negate = TRUE)) %>%
  tab_survey(q7_no_routine_vacc_r) %>%
  # rename columns appropriately
  select("Reasons" = value, 
         "Routine (n)" = n , 
         "% (95% CI)" = ci)

## campaign reasons 
campaign <- survey_design %>% 
  ## filter for not vaccinated 
  filter(str_detect(vaccine_mass, pattern = fixed("Yes -"), negate = TRUE)) %>%
  tab_survey(q28_no_campaign_vacc_r) %>% 
  ## rename remaining columns appropriately 
  select("Campaign (n)" = n, 
         "% (95% CI)" = ci)
  
## bind two together 
bind_cols(routine, 
          campaign) %>% 
  kable(digits = 1)

```


Weighted counts and proportions for reasons not vaccinated in supplemented 
immunisation activities, among those not vaccinated

<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// no_vacc_reason_sia \\\
--------------------------------------------------------------------------------

The below chunk creates a weighted table of counts proportions for reasons 
not vaccinated during supplemented immunisation activitites. 

Note that low counts or short observation times may lead to a confidence interval 
that crosses zero (i.e. negative) for mortality ratios. These should be interpreted
as if no deaths or recoded to zero (impossible to have negative deaths). 
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->
```{r no_vacc_reason_sia}

survey_design %>% 
  filter(str_detect(vaccine_sia, pattern = fixed("Yes -"), negate = TRUE)) %>%
  tab_survey(q38_no_sia_vacc_reason) %>%
  ## rename columns appropriately
  select("Reasons" = value, 
         "Routine (n)" = n , 
         "% (95% CI)" = ci) %>%
  kable(digits = 1)
```

