---
title: "Beboto vaccination coverage survey"
output: 
  word_document:
    keep_md: true
---

## Installing and loading required packages 

<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// setup \\\
-------------------------------------------------------------------------------->

```{r setup, include = FALSE, results='hide', message=FALSE, warning=FALSE}

## hide all code chunks in the output, but show errors, define figure width/height
knitr::opts_chunk$set(echo = FALSE, error = TRUE)


## Installing required packages for this template
required_packages <- c("knitr",       # create output docs
                       "here",        # find your files
                       "rio",         # for importing data
                       "epitrix",     # clean/shape data
                       "dplyr",       # clean/shape data
                       "tidyr",       # clean/shape data
                       "forcats",     # manipulate and rearrange factors
                       "stringr",     # manipulate texts
                       "ggplot2",     # create plots and charts
                       "sitrep",      # MSF field epi functions
                       "survey",      # for survey functions
                       "srvyr",       # dplyr wrapper for survey package
                       "flextable",   # for prettier tables
                       "viridis",     # for pretty colour palettes
                       "matchmaker")  # for easier excel cleaning   
                       

for (pkg in required_packages) {
  ## install packages if not already present
  if (!pkg %in% rownames(installed.packages())) {
    install.packages(pkg)
  }
  
  ## load packages to this current session 
  library(pkg, character.only = TRUE)
}

```

<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// read_data \\\
--------------------------------------------------------------------------------
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r read_data  merge data, warning = FALSE, message = FALSE}

## Excel file ------------------------------------------------------------------

## read in household data sheet
study_data_hh <- rio::import(here::here("data", "vaccination_coverage_cleaned.xlsx"), 
                             which = "hh level", na = ".")

## read in individual level data sheet
study_data_indiv <- rio::import(here::here("data", "vaccination_coverage_cleaned.xlsx"), 
                                which = "ind level", na = ".")

## join the individual and household data to form a complete data set
study_data_raw <- left_join(study_data_hh, study_data_indiv, by = "merge_id")


## make a copy of your orginal dataset and name it study_data_cleaned
study_data_cleaned <- study_data_raw

```

<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// browse_data \\\
--------------------------------------------------------------------------------
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r browse_data, eval = FALSE, include = FALSE}

##Julia note: this is weird, it's returning ages that are fine (e.g. age of routine vaccination is 9 months and current age is 11 months. That's normal...)

## check for logical date inconsistencies 
## for example check vaccination age greater than current age and return corresponding IDs


study_data_cleaned$age_routine_vacc <- as.numeric(study_data_cleaned$age_routine_vacc)

study_data_cleaned$age_months <- as.numeric(study_data_cleaned$age_months)

study_data_raw %>% 
  filter(age_routine_vacc > age_months) %>%
  select("merge_id", "age_routine_vacc", "age_months")


```

<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// standardise_dates \\\
--------------------------------------------------------------------------------
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->


```{r standardise_dates, include = FALSE}

## use the guess_dates() function to make a first pass at date variables.
study_data_cleaned <- study_data_cleaned %>%
   mutate_at(vars(matches("date|Date")), linelist::guess_dates,
             error_tolerance = 0.5)

#checked class of "today" date variable - it's character. 
class(study_data_cleaned$today)

#change "today" date variable to a date:
study_data_cleaned$today<- as.Date(study_data_cleaned$today, format = "%Y-%m-%d")

#drop data from training and pilot day. 
table(study_data_cleaned$today) # check which dates need to be dropped
#drop dates older than April 1, 2020
study_data_cleaned <- subset(study_data_cleaned, today >= "2020-04-01")

```

##RETURN to this later and do all the cleaning in R 


```{r cleaning, include = FALSE}

#checked in excel to find weirdness for variables, like we did each day during survey. Corrected hh number, cluster number, and team number for some. 

#checking for weirdness here & corrected in excel if necessary
#any houshold marked as both first AND second visit on the same line. 
#table(study_data_cleaned$first_visit, study_data_cleaned$second_visit)

#any empty hh that gave consent
#table(study_data_cleaned$empty_household, study_data_cleaned$consent)

#remove space from ndaba3:
study_data_cleaned$village_name <- gsub(pattern = "ndaba 3",replacement = "ndaba3", study_data_cleaned$village_name)


#changed character variables that I'll be using to numeric: 
study_data_cleaned$children_count <- as.numeric(study_data_cleaned$children_count)
study_data_cleaned$cluster_number <- as.numeric(study_data_cleaned$cluster_number)
study_data_cleaned$household_number <- as.numeric(study_data_cleaned$household_number)
study_data_cleaned$age_caretaker <- as.numeric(study_data_cleaned$age_caretaker)

```

```{r recoding age}

#using matchmaker, I <3 matchmaker
#https://www.repidemicsconsortium.org/matchmaker/

# importing data dictionary I created to recode "other" values for all three variables.
dict_data_cleaning <- rio::import(here::here("data", "dict_data_cleaning.xlsx"))

#creating new variables for age so I don't overwrite existing ones (since new group I'll create below is character and I also want to keep the numeric)
study_data_cleaned <- study_data_cleaned %>%
  mutate(age_months1 = age_months,
         age_years1 = age_years)

# using matchmaker package and data dictionary I created to recode age values
study_data_cleaned <- match_df(study_data_cleaned,
  dictionary = dict_data_cleaning,
  from = "options",
  to = "values",
  by = "grp")

#merge two columns of months and years into one for data visualization later: 
study_data_cleaned <- study_data_cleaned %>%
  mutate(age_character = case_when (
    age_months1 == "6m" ~ "6m",
    age_months1 == "7m" ~ "7m",
    age_months1 == "8m" ~ "8m",
    age_months1 == "9m" ~ "9m",
    age_months1 == "10m" ~ "10m",
    age_months1 == "11m" ~ "11m",
    age_years1 == 0 ~ NA_character_, # there were still ages coded with 0 even though their values were in months
    TRUE ~ age_years1)) # for all other instances, fill in the new column with data age_years column 


```


```{r recoding "other" reasons for non-vaccination}

# creating dataframes with all other reasons. Create and export to make matchmaker data dictionary thingie. 
#https://www.repidemicsconsortium.org/matchmaker/
  
msf_other <- study_data_cleaned %>%
  filter(!is.na(reason_msf_other)) %>%
  group_by(reason_msf_other) %>%
  summarise(n = n())

sia_other <- study_data_cleaned %>%
  filter(!is.na(reason_sia_other)) %>%
  group_by(reason_sia_other) %>%
  summarise(n = n())

routine_other <- study_data_cleaned %>%
  filter(!is.na(reason_route_other)) %>%
  group_by(reason_route_other) %>%
  summarise(n = n())

# exporting these to combine and work on for matchmaker
rio::export(msf_other, str_glue("msf_other_reasons_{Sys.Date()}.xlsx"))
rio::export(sia_other, str_glue("sia_other_reasons_{Sys.Date()}.xlsx"))
rio::export(routine_other, str_glue("routine_other_reasons_{Sys.Date()}.xlsx"))

# importing data dictionary I created to recode "other" values for all three variables.
dict_other_reasons <- rio::import(here::here("data", "dict_other_reasons.xlsx"))

# using matchmaker package and data dictionary I created to recode "other" values for all three variables.
study_data_cleaned <- match_df(study_data_cleaned,
  dictionary = dict_other_reasons,
  from = "options",
  to = "values",
  by = "grp")


```


```{r describing households - with paper forms}

#read in the daily household journal summary sheet
hh_summary <- rio::import(here::here("data", "journal_menage.xlsx"))


# EXLCUDING row 30, FERRICK KACHALA
hh_summary <- hh_summary[-c(30),] 


# number hh visited in total.  
total_hh <- sum(hh_summary$n_hh_visited)

# number hh requiring second visit
sum(hh_summary$`n_hh_requiring two visits`)
# % hh requiring second visit
(sum(hh_summary$`n_hh_requiring two visits`))/(sum(hh_summary$n_hh_visited))*100

#number hh empty first visit
sum(hh_summary$n_hh_empty_1st_visit)
#% hh empty first visit
(sum(hh_summary$n_hh_empty_1st_visit))/(sum(hh_summary$n_hh_visited)) *100

# number hh no person to consent first visit
sum(hh_summary$n_hh_no_adult_1st_visit)-17 #removed the 17 households that were empty, as they were included in having no one to consent. I just want to see houshold that weren't empty, but still had no one able to provide consent. 
# % hh no person to consent first visit
(sum(hh_summary$n_hh_no_adult_1st_visit)-17)/(sum(hh_summary$n_hh_visited))*100

# number hh empty second visit
sum(hh_summary$n_hh_empty_2nd_visit)
# percent hh empty second visit
(sum(hh_summary$n_hh_empty_2nd_visit))/(sum(hh_summary$`n_hh_requiring two visits`))*100

#number hh no person to consent second visit
sum(hh_summary$n_hh_no_adult_2nd_visit)-8 #removed the 8 households that were empty on the seond visit, as they were included in having no one to consent. I just want to see houshold that weren't empty, but still had no one able to provide consent. 
(sum(hh_summary$n_hh_no_adult_2nd_visit)-8)/(sum(hh_summary$`n_hh_requiring two visits`))*100

#number and percent with no children of eligible age. (not including NAs because that indicates the interview didn't get that far - the hh was empty or no one to consent)
study_data_cleaned  %>%
  group_by(children_count == 0) %>%
  summarise(n= n()) %>%
  mutate(percent = (n /total_hh)*100) %>%
  mutate(percent = round(percent, 2))

# number of households interviewed (source: paper copies of daily hh journal (=329). 
#HOWEVER, this does match with Kobo data, so we go with kobo data since that is the number of interviews completed for certain) Code for paper data was: sum(hh_summary$n_hh_interviewed)


#bfore using kobo data, drop the "other" villages that we'll exlude for total interviews. 

# number of hh interivewed from kobo data (= 321)
hh_interviewed <- study_data_cleaned %>%
  filter(children_count != 0) %>%
  filter(village_name != "other") %>%
  group_by(village_name, household_number) %>%
  select(village_name, household_number, children_count) %>%
  summarise(count = n()) %>%
  nrow()
  

# number of hh interviewed on 1st visit (= # hh interviewed - hh empty/no adult)
first_visit_interview <- (hh_interviewed - 48)
# number of hh interviewed on 2nd visit (= # hh interviewed - hh empty/no adult)
hh_interviewed-first_visit_interview #number calculated in step above


# 48 hh empty on first visit, 27 still empty on second visit
48-27 # = 21: number of households definitely not interviewed on either first or second visit, since empty or no consent on both occassions. 



#overall response rate: 
(hh_interviewed/total_hh)*100


# households that were possible to interview (therefore interviewed) on second visit: hh needing a second visit - hh still empty - hh still no adult
48-8-19 # = 21

# therefore number interviewed on 1st visit is total interviewed - households interviewed on second visit
321-21 # = 300


```

```{r describing households - using Kobo data only}

#this data is unreliable and has much lower counts than was traced on the paper form. I don't think surveyors were truly recording all 1st visits to a hh in kobo. 
table(study_data_cleaned$first_visit)

table(study_data_cleaned$second_visit)

table(study_data_cleaned$empty_household)



```



```{r household characteristic table}
#create data frame with values above and pass to flextable for prettier report.  
#IN PRORGESS. Fake numbers and needs work. 

data.frame(Characteristic = c("Total households interviewed", 
                              "Households interviewed - 1st visit",
                              "Households interviewed - 2nd vist",
                              "Households requiring second visit", 
                              "Households not possible to interview after two visits",
                              "Households without eligible children",
                              "Households that did not consent", 
                              "Total households visited"), 
                              count = c(321, 
                                        300,
                                        21,
                                        48, 
                                        27, 
                                        75, 
                                        1, 
                                        438)) %>%
  rename("Count (n)" = count) %>%
  flextable() %>%
  autofit





```

<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// remove_unused_data \\\
--------------------------------------------------------------------------------
It is important that you drop observations before adding survey weights!
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r remove_unused_data}

## store the cases that you drop so you can describe them (e.g. non-consenting)
dropped <- study_data_cleaned %>% 
  filter(consent =="no")

#drop the clusters used to replace the ferrick that was not accessible. Do not have population counts for those villages. 
dropped2 <- study_data_cleaned %>%
  filter(village_name == "other")

## drop the unused rows from the survey data set  
study_data_cleaned <- study_data_cleaned %>%
  filter(village_name != "other") %>%
  filter(consent == "yes")

```



```{r filtering for no children}

study_data_cleaned <- study_data_cleaned %>%
  filter(!is.na(child_number)) #filtering for no children, indicating no child of eligible age or no one home, etc.) 

```

<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// factor_vars \\\
--------------------------------------------------------------------------------
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->


##Relabelling, reordering 

```{r vaccination status msf/routine/sia}

## MSF vaccination - combine yes answers into one - yes card and yes verbal
study_data_cleaned <- study_data_cleaned %>% 
  mutate(msf_vacc_status = case_when(
    is.na(msf_vacc) ~ NA_character_,
    msf_vacc == "card" ~ "Yes", 
    msf_vacc == "verbal" ~ "Yes", 
    msf_vacc == "no" ~ "No", 
    msf_vacc == "dont_know" ~ "Don't know", 
    msf_vacc == "no_answer" ~ "No answer"))

#checking the variable we created above. 
table(study_data_cleaned$msf_vacc) #old variable
table(study_data_cleaned$msf_vacc_status) #new variable


## ROUTINE vaccination - combine yes answers into one - yes card and yes verbal
study_data_cleaned <- study_data_cleaned %>% 
  mutate(routine_vacc_status = case_when(
    is.na(routine_vacc) ~ NA_character_,
    routine_vacc == "card" ~ "Yes", 
    routine_vacc == "verbal" ~ "Yes", 
    routine_vacc == "no" ~ "No", 
    routine_vacc == "dont_know" ~ "Don't know", 
    routine_vacc == "no_answer" ~ "No answer"))

#checking the variable we created above.
table(study_data_cleaned$routine_vacc) # old variable
table(study_data_cleaned$routine_vacc_status) # new variable


## SIA vaccination - combine yes answers into one - yes card and yes verbal
study_data_cleaned <- study_data_cleaned %>% 
  mutate(sia_vacc_status = case_when(
    is.na(sia_vacc) ~ NA_character_,
    sia_vacc == "card" ~ "Yes", 
    sia_vacc == "verbal" ~ "Yes", 
    sia_vacc == "no" ~ "No", 
    sia_vacc == "dont_know" ~ "Don't know", 
    sia_vacc == "no_answer" ~ "No answer"))

#checking the variable we created above.
table(study_data_cleaned$sia_vacc) # old variable
table(study_data_cleaned$sia_vacc_status) # new variable


```




```{r overall vaccination status}

#creating variable for all vaccinations combined for overall coverage
study_data_cleaned <- study_data_cleaned %>%
  mutate(overall_vacc_status = case_when (
    sia_vacc_status == "Yes" ~ "Vaccinated",
    msf_vacc_status == "Yes" ~ "Vaccinated",
    routine_vacc_status == "Yes" ~ "Vaccinated", 
    TRUE ~ "Not Vaccinated"))

#checking new variable
table(study_data_cleaned$overall_vacc_status)
  
```

```{r immunity status}

#creating variable for immunity based on if they were previously ill or vaccinated. 
study_data_cleaned <- study_data_cleaned %>% 
  mutate(immunity = case_when(
    diagnosis_disease == "yes" ~ "Immune", 
    overall_vacc_status == "Yes" ~ "Immune", 
    TRUE ~ "Susceptible")) 

```



```{r reasons for non-vaccination - MSF}

# Relabel reasons

# check which reasons are used for MSF
table(study_data_cleaned$reason_msf_vacc)

#rename reasons for MSF
study_data_cleaned <- study_data_cleaned %>% 
  mutate(msf_reason_renamed = case_when(
    is.na(msf_vacc) ~ NA_character_,
    reason_msf_vacc == "family_away" ~ "Family was outside village during campaign", 
    reason_msf_vacc == "other" ~ "Other", 
    reason_msf_vacc == "unaware_eligible" ~ "Didn't know child was eligible for vaccination"))

#check old and new variables together
table(study_data_cleaned$reason_msf_vacc)
table(study_data_cleaned$msf_reason_renamed)
table(study_data_cleaned$reason_msf_other)


# creating a variable with ALL msf reasons together - including "other."

study_data_cleaned <- study_data_cleaned %>%
  mutate(msf_all_reasons = case_when (
    reason_msf_vacc == "other" ~ reason_msf_other, # when the kobo data indicates "other" in the reason column, then fill this new variable with data from the kobo "reason_msf_other" column
                          TRUE ~ msf_reason_renamed)) # for all other instances, fill in the new column with data from the kobo reason_msf_vacc column (or more specifically the one I created with better names for graphing. 
 

```



``` {r reasons for non-vaccination - routine}
# Relabel reasons

#check which reasons are used for routine
table(study_data_cleaned$reason_route_vacc)

## rename routine reasons 
study_data_cleaned <- study_data_cleaned %>% 
  mutate(route_reason_renamed = case_when(
    is.na(reason_route_vacc) ~ NA_character_,
    reason_route_vacc == "child_old" ~ "Child was too old", 
    reason_route_vacc == "child_young" ~ "Child was too young", 
    reason_route_vacc == "other" ~ "Other", 
    reason_route_vacc == "no_answer" ~ "No answer", 
    reason_route_vacc == "not_beneficial" ~ "Not beneficial", 
    reason_route_vacc == "painful" ~ "Painful"))


#check old and new variable
table(study_data_cleaned$reason_route_vacc)
table(study_data_cleaned$route_reason_renamed)


#routine other reasons: # need to find a way to group some of these with similar spellings/ reasons
routine_reason_other <- study_data_cleaned %>%
  filter(!is.na(reason_route_other)) %>%
  group_by(reason_route_other) %>%
  summarise(reason = n())


# creating a variable with ALL routine reasons together - including "other."
study_data_cleaned <- study_data_cleaned %>%
  mutate(route_all_reasons = case_when (
    reason_route_vacc == "other" ~ reason_route_other, # when the kobo data indicates "other" in the reason column, then fill this new variable with data from the kobo "reason_msf_other" column
                          TRUE ~ route_reason_renamed))# for all other instances, fill in the new column with data from the kobo reason_msf_vacc column (or more specifically the one I created with better names for graphing. 


```

```{r reasons for non-vaccination - SIA}
# Relabel reasons

#check which reasons are used for SIA
table(study_data_cleaned$reason_sia_vacc)

## rename SIA reasons 
study_data_cleaned <- study_data_cleaned %>% 
  mutate(sia_reason_renamed = case_when(
    is.na(reason_sia_vacc) ~ NA_character_,
    reason_sia_vacc == "distance" ~ "Vaccination site was too far away", 
    reason_sia_vacc == "family_away" ~ "Family was away during time of vaccination", 
    reason_sia_vacc == "no_answer" ~ "No answer", 
    reason_sia_vacc == "other" ~ "Other", 
    reason_sia_vacc == "unaware_campaign" ~ "Unaware there was a vaccination campaign",
    reason_sia_vacc == "unaware_eligible" ~ "Didn't know child was eligible for vaccination"))

#check old and new variable
table(study_data_cleaned$reason_sia_vacc)
table(study_data_cleaned$sia_reason_renamed)
  
#SIA other reasons: # need to find a way to group some of these with similar spellings/ reasons
sia_reason_other <- study_data_cleaned %>%
  filter(!is.na(reason_sia_other)) %>%
  group_by(reason_sia_other) %>%
  summarise(reason = n())


# creating a variable  with ALL SIA reasons together - including "other."
study_data_cleaned <- study_data_cleaned %>%
  mutate(sia_all_reasons = case_when (
    reason_sia_vacc == "other" ~ reason_sia_other, # when the kobo data indicates "other" in the reason column, then fill this new variable with data from the kobo "reason_msf_other" column
                          TRUE ~ sia_reason_renamed)) # for all other instances, fill in the new column with data from the kobo reason_msf_vacc column (or more specifically the one I created with better names for graphing. 

```

```{r reordering factors}

## correct the order of levels in newly created variables:

#MSF vaccination
study_data_cleaned <- study_data_cleaned %>% 
  mutate(msf_vacc_status = fct_relevel(msf_vacc_status, 
                                       "Yes", 
                                       "No", 
                                       "Don't know",
                                       "No answer"))

#ROUTINE vaccination
study_data_cleaned <- study_data_cleaned %>% 
  mutate(routine_vacc_status = fct_relevel(routine_vacc_status, 
                                       "Yes", 
                                       "No", 
                                       "Don't know", 
                                       "No answer"))

#SIA vaccination
study_data_cleaned <- study_data_cleaned %>% 
  mutate(sia_vacc_status = fct_relevel(sia_vacc_status, 
                                       "Yes", 
                                       "No", 
                                       "Don't know", 
                                       "No answer"))

#overall vaccination
study_data_cleaned <- study_data_cleaned %>% 
  mutate(overall_vacc_status = fct_relevel(overall_vacc_status, 
                                       "Yes", 
                                       "No"))

#previous measles diagnosis: 

study_data_cleaned <- study_data_cleaned %>% 
  mutate(diagnosis_disease = fct_relevel(diagnosis_disease, 
                                       "yes", 
                                       "no", 
                                       "dont_know"))

#immunity
study_data_cleaned <- study_data_cleaned %>% 
  mutate(immunity = fct_relevel(immunity, 
                                       "Immune", 
                                       "Susceptible"))



```
<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// cluster_counts \\\
--------------------------------------------------------------------------------
You will need to have one column with a cluster identifier which 
matches your survey data, and another column with the number of households in 
each cluster. 
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->
##Survey weights
```{r cluster_counts}

#read data in
cluster_counts <- rio::import(here::here("data", "cluster counts.xlsx"))

#round digits
cluster_counts$total_hh<- round(cluster_counts$total_hh, digits = 0)

#lowercase
cluster_counts$village_name <- tolower(cluster_counts$village_name) 

#drop population column
cluster_counts <- cluster_counts %>%
    select(-pop)

#might need to be a tibble for code later? the template had this created as a tibble but I imported instead. 
as_tibble(cluster_counts)


```


<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// survey_weights \\\
--------------------------------------------------------------------------------
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r survey_weights}

## merge village and household to create a unique household ID 
study_data_cleaned <- study_data_cleaned %>% 
  mutate(hh_id = str_glue("{village_name}_{household_number}"))

## create cluster weights 
#https://rdrr.io/github/R4EPI/sitrep/man/add_weights_cluster.html

study_data_cleaned <- add_weights_cluster(x = study_data_cleaned, 
                                          cl = cluster_counts, 
                                          eligible = children_count, 
                                          interviewed = children_count, 
                                          cluster_x = village_name, 
                                          cluster_cl = village_name, 
                                          household_x = household_number, 
                                          household_cl = total_hh, 
                                          surv_weight = "surv_weight_cluster", 
                                          surv_weight_ID = "surv_weight_ID_cluster", 
                                          ignore_cluster = FALSE, 
                                          ignore_household = FALSE)


```



<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// survey_design \\\
--------------------------------------------------------------------------------

Create survey object according to your study design. Used the same way as dataframes to calculate weight proportions etc. 
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r create_survey_design}

survey_design <- study_data_cleaned %>% 
  as_survey_design(ids = village_name, # 1 for no cluster ids 
                   weights = surv_weight_cluster, # weight variable created above 
                   strata = NULL # sampling was simple (no strata)
                  )


```



<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// save_cleaned_data \\\
--------------------------------------------------------------------------------

You can save your cleaned dataset as an Excel. 
This automatically names your file "study_data_cleaned_DATE", where DATE is the
current date.
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r save_cleaned_data}
rio::export(study_data_cleaned, str_glue("study_data_cleaned_{Sys.Date()}.xlsx"))
```



# Results

## Survey inclusion 


<!--~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// inclusion_counts \\\
--------------------------------------------------------------------------------

The below chunks calculate values that are displayed with the inline text

Get the counts of clusters and households included 
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~-->

```{r inclusion_counts}

## get counts of number of clusters 
num_clus <- study_data_cleaned %>%
  ## trim data to unique clusters
  distinct(cluster_number) %>% 
  ## get number of rows (count how many unique)
  nrow()

## get counts of number households 
num_hh <- study_data_cleaned %>% 
  ## get unique houses by cluster
  distinct(cluster_number, household_number) %>% 
  ## get number of rounds (count how many unique)
  nrow()

```


We included `r num_hh` households accross `r num_clus` clusters in this survey analysis. 


Among the `r nrow(dropped)` individuals without consent to participate in the survey, 
the reasons for refusal are ___________. 

<!--~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// cluster_hh_size \\\
--------------------------------------------------------------------------------

The below chunks calculate values that are displayed with the inline text

Get counts of households per cluster and individuals per household. 
From these create medians and standard deviations. 
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~-->

```{r cluster_hh_size}

## get counts of the number of households per cluster
clustersize <- study_data_cleaned %>% 
  ## trim data to only unique households within each cluster
  distinct(cluster_number, household_number) %>%
  ## count the number of households within each cluster
  count(cluster_number) %>% 
  pull(n)

## get the median number of households per cluster
clustermed <- median(clustersize)

## get the min and max number of households per cluster
## paste these together seperated by a dash 
clusterrange <- str_c(range(clustersize), collapse = "--")

## get counts of children per household 
## do this by cluster as household IDs are only unique within clusters
hhsize <- study_data_cleaned %>% 
  count(cluster_number, household_number) %>%
  pull(n) 

## get median number of children per household
hhmed <- median(hhsize)
## get the min and max number of children per household
## paste these together seperated by a dash 
hhrange <- str_c(range(hhsize), collapse = "--")

# get standard deviation 
hhsd <- round(sd(hhsize), digits = 1)
```


The median number of households per cluster was
`r clustermed`, with a range of `r clusterrange`. The median number of children
per household was `r hhmed` (range: `r hhrange`, standard deviation: `r hhsd`). 


## Demographic information


In total we included `r nrow(study_data_cleaned)` children in the survey analysis. 
The age breakdown and a comparison with the source population is shown below. 


```{r median_age_sex_ratios}
## compute the median age; first need to convert ages to one tyoe of format (chose to make all ages in years)
study_data_cleaned <- study_data_cleaned %>%
  mutate(age_new = case_when(
    age_months == 6 ~ 0.5,
    age_months == 7 ~ 0.58, 
    age_months == 8 ~ 0.67, 
    age_months == 9 ~ 0.75, 
    age_months == 10 ~ 0.83,
    age_months == 11 ~ 0.92, 
    age_years == 1 ~ 1, 
    age_years == 2 ~ 2, 
    age_years == 3 ~ 3, 
    age_years == 4 ~ 4, 
    age_years == 5 ~ 5, 
    age_years == 6 ~ 6,
    age_years == 7 ~ 7,
    age_years == 8 ~ 8,
    age_years == 9 ~ 9))

medage <- median(study_data_cleaned$age_new)

#children >= 5
fmt_count(study_data_cleaned, age_new >= 5)
# children under 5
fmt_count(study_data_cleaned, age_new < 5)
# children under 1
fmt_count(study_data_cleaned, age_new < 1)


## paste the lower and uper quartile together
iqr <- str_c(  # basically copy paste together the following
  ## calculate the 25% and 75% of distribution, with missings removed
  quantile(     
    study_data_cleaned$age_new, 
    c(0.25, 0.75), 
    na.rm = TRUE), 
  ## between lower and upper place an en-dash
  collapse = "--")


## compute overall sex ratio 
sex_ratio <- study_data_cleaned %>% 
  count(sex) %>%
  pivot_wider(names_from = sex, values_from = n) %>% 
  mutate(ratio = round(male/female, digits = 3)) %>%
  pull(ratio)


```

Among the `r nrow(study_data_cleaned)` surveyed individuals, there were 
`r fmt_count(study_data_cleaned, sex == "female")` females and 
`r fmt_count(study_data_cleaned, sex == "male")` males (unweighted). The male to
female ratio was `r sex_ratio` in the surveyed population.
The median age of surveyed individuals was `r medage` years (Q1-Q3 of `r iqr`
years). Children under five years of age made up 
`r fmt_count(study_data_cleaned, age_new < 5)`of the surveyed individuals. Children under one year made up `r fmt_count(study_data_cleaned, age_new < 1)`

```{r age pyramid}

#need age_character to be a factor to create age pyramid
study_data_cleaned$age_character <- factor(study_data_cleaned$age_character, 
                                           c("6m", "7m", "8m", "9m", "10m", "11m", "1y", "2y","3y", "4y", "5y", "6y", "7y", "8y", "9y"))

#cleaning up pyramid a bit by creating 
study_data_cleaned$age_character<- recode(study_data_cleaned$age_character,
                             "6m" = "6-11m",
                             "7m" ="6-11m",
                             "8m" = "6-11m",
                             "9m" = "6-11m",
                             "10m" = "6-11m",
                             "11m" = "6-11m",
                             "1y" = "1-3y",
                             "2y" = "1-3y",
                             "3y" = "1-3y",
                             "4y" = "4-6y",
                             "5y" = "4-6y",
                             "6y" = "4-6y",
                             "7y" = "7-9y",
                             "8y" = "7-9y",
                             "9y" = "7-9y")
                                       

plot_age_pyramid(study_data_cleaned,
                  age_group = "age_character", 
                  split_by = "sex", 
                 na.rm = TRUE) + 
  labs(y = "Children (n)", x = "Age") + # change axis  labels
  theme_classic() +
  theme(legend.position = "bottom",     # move legend to bottom
        legend.title = element_blank(), # remove title
        text = element_text(size = 18)  # change text size
       )  +
     scale_fill_viridis_d(begin = 0.7, end = 0.3)

```
<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// describe_by_age_group_and_sex \\\
--------------------------------------------------------------------------------

This chunk will create an unweighted table of survey individuals by age group 
and sex.

Note that proportions are of the total sample (not within each gender) 
to change this, set proptotal = FALSE
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r describe_by_sex}

tab_linelist(study_data_cleaned, age_group, 
             strata     = sex, 
             row_total  = TRUE,
             prop_total = TRUE) %>%
  ## select and rename column names appropriately
  select("Age"              = "value",
         "Female cases (n)" = "female n",
         "Female %"         = "female proportion",
         "Male cases (n)"   = "male n",
         "Male %"           = "male proportion",
         "Total") %>%
  flextable() %>%
  autofit

```

```{r describe respondents}

# who is respondent
study_data_cleaned %>%
  group_by(caretaker) %>%
  summarise(n= n()) %>%
  arrange(desc(n)) %>%
  mutate(prop = (n/sum(n))) %>%
  mutate(prop = round(prop, 3)*100) %>%
  flextable() %>%
  autofit

# median age of respondent
median(study_data_cleaned$age_caretaker)


```




## Vaccination coverage

Weighted vaccination coverage; accepting equal validity from self-reported and 
card-reported vaccination status

<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// vaccination_coverage_overall \\\
--------------------------------------------------------------------------------

The below chunk creates a weighted table of counts proportions for vaccination 
coverage while accpeting equal validity from self- and card-reporting. 

Note that this includes a design effect. 

Note that low counts or short observation times may lead to a confidence interval 
that crosses zero (i.e. negative) for mortality ratios. These should be interpreted
as if no deaths or recoded to zero (impossible to have negative deaths). 
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r msf_vaccination_coverage}

## coverage by card and verbal together

survey_design %>%  # use the survey object (weighted)
  ## calculate weighted counts and weighted proportions
  tab_survey(msf_vacc_status, deff = TRUE) %>%
  ## select and rename appropriate columns 
  select("MSF vaccination status" = value, 
         "Children (n)" = n, 
         "Vaccination coverage (95% CI)" = ci,
         "Design effect" = deff) %>%
  flextable () %>%
  colformat_num(col_keys = c("Design effect"), digits = 1) %>%
  autofit

#getting just number of children for each vaccination status value
study_data_cleaned %>%
tab_linelist(msf_vacc_status)


## coverage by card and verbal separately
survey_design %>%  # use the survey object (weighted)
  ## calculate weighted counts and weighted proportions
  tab_survey(msf_vacc, deff = TRUE) %>%
  ## select and rename appropriate columns 
  select("MSF vaccination status" = value, 
         "Children (n)" = n, 
         "Vaccination coverage (95% CI)" = ci,
         "Design effect" = deff) %>%
  flextable () %>%
  colformat_num(col_keys = c("Design effect"), digits = 1) %>%
  autofit

# vaccination site, unweighted: 
study_data_cleaned %>%
  tab_linelist(place_msf_vacc)


```


```{r routine_vaccination_coverage}


# routine vaccination coverage: 
survey_design %>%  # use the survey object (weighted)
  ## calculate weighted counts and weighted proportions
    tab_survey(routine_vacc_status, deff = TRUE) %>%
  ## select and rename appropriate columns 
  select("Routine vaccination status" = value, 
         "Children (n)" = n, 
         "Vaccination coverage (95% CI)" = ci,
         "Design effect" = deff) %>%
  flextable () %>%
  colformat_num(col_keys = c("Design effect"), digits = 1) %>%
  autofit


## coverage by card and verbal separately

survey_design %>%  # use the survey object (weighted)
  ## calculate weighted counts and weighted proportions
  tab_survey(routine_vacc, deff = TRUE) %>%
  ## select and rename appropriate columns 
  select("Routine vaccination status" = value, 
         "Children (n)" = n, 
         "Vaccination coverage (95% CI)" = ci,
         "Design effect" = deff) %>%
  flextable () %>%
  colformat_num(col_keys = c("Design effect"), digits = 1) %>%
  autofit

#getting just number of children for each vaccination status value
study_data_cleaned %>%
tab_linelist(routine_vacc_status)

# vaccination site, unweighted: 
study_data_cleaned %>%
  tab_linelist(place_routine_vacc)





```



```{r sia_vaccination_coverage}

# SIA vaccination coverage: 
survey_design %>%  # use the survey object (weighted)
  ## calculate weighted counts and weighted proportions
  tab_survey(sia_vacc_status, deff = TRUE) %>%
  ## select and rename appropriate columns 
  select("SIA vaccination status" = value, 
         "Children (n)" = n, 
         "Vaccination coverage (95% CI)" = ci,
         "Design effect" = deff) %>%
  flextable() %>%
  colformat_num(col_keys = c("Design effect"), digits = 1) %>%
  autofit

## coverage by card and verbal separately
survey_design %>%  # use the survey object (weighted)
  ## calculate weighted counts and weighted proportions
  tab_survey(sia_vacc, deff = TRUE) %>%
  select("SIA vaccination status" = value, 
         "Children (n)" = n, 
         "Vaccination coverage (95% CI)" = ci,
         "Design effect" = deff) %>%
  flextable() %>%
  colformat_num(col_keys = c("Design effect"), digits = 1) %>%
  autofit
  

#getting just number of children for each vaccination status value
study_data_cleaned %>%
tab_linelist(sia_vacc_status)





```

<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// vaccination_coverage_overall_detail \\\
--------------------------------------------------------------------------------
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r overall coverage - all vacc oppotunities}

# overall vaccination coverage: 
survey_design %>%  # use the survey object (weighted)
  ## calculate weighted counts and weighted proportions
  tab_survey(overall_vacc_status, deff = TRUE) %>%
  ## select and rename appropriate columns 
  select("Overall vaccination status" = value, 
         "Children (n)" = n, 
         "Vaccination coverage (95% CI)" = ci,
         "Design effect" = deff) %>%
  flextable () %>%
  colformat_num(col_keys = c("Design effect"), digits = 1) %>%
  autofit

#getting just number of children for each vaccination status value
study_data_cleaned %>%
tab_linelist(overall_vacc_status)

```


```{r overall coverage graph, warning = FALSE, echo = FALSE}

all_coverage <- data.frame(vacc_campaign = c("MSF vaccination campaign",
                                             "Routine vaccination (9 months)",
                                             "Other vaccination opportunities",
                                             "Overall vaccination coverage"), 
                           coverage = c(95.8, 45.4, 48, 98.1), 
                           lower_ci = c(93.0, 35.0, 38.3, 96.3),
                           upper_ci = c(97.5, 56.1, 57.8, 99.1))

all_coverage %>%
  ggplot(aes(x = reorder(vacc_campaign, -coverage), y = coverage, fill = vacc_campaign)) +
  geom_col() +
  labs(x = "Measles vaccination opportunity",
       y= "Measles vaccination coverage (%)") + 
  theme_classic() +
  theme(axis.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        legend.position="none") + 
  scale_fill_viridis_d(begin = 0.2, end = 0.6) +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2) +
  geom_hline(aes(yintercept = 95, colour = "orange", label = "hi")) +
  scale_x_discrete(labels = function(vacc_campaign) str_wrap(vacc_campaign, width = 10)) # wrapping axis text with long labels


```



## Reasons for not vaccinating - weighted tables and graphs

Weighted counts and proportions for reasons not vaccinated in routine and 
campaign circumstances, individually, among those not vaccinated
<!-- ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
/// no_vacc_reason_routine_campaign_combo \\\
--------------------------------------------------------------------------------
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

```{r No vaccination - MSF reasons, weighted & GRAPH}

## msf reasons - with the variable msf_all_reasons - where "other" is now recoded
msf_all_reasons <- survey_design %>% 
  # filter for those not vaccinated 
  filter(str_detect(msf_vacc_status, pattern = fixed("Yes"), negate = TRUE)) %>%
  tab_survey(msf_all_reasons)  %>%
  # rename columns appropriately if you want, pipe code above.
  select("reasons_msf" = value, 
         "Children (n)" = n, 
         "Percent (95% CI)" = ci) %>%
  mutate(prop = `Children (n)`/sum(`Children (n)`)*100) %>% # using this column for graphing later
  mutate(prop = round(prop, 1))

#print table
msf_all_reasons %>%
  flextable() %>%
  autofit()

#just number of children who did not receive vaccination
table(study_data_cleaned$msf_vacc_status)
  

##graph of the MSF reasons (including OTHER, recoded. column created in chunk 16);
msf_all_reasons %>%
  ggplot(aes(x = reorder(reasons_msf, -prop), y = prop, fill = reasons_msf)) +
  geom_bar(stat ='identity') +
  scale_fill_viridis_d(begin = 0.7, end = 0.3) + 
  theme_classic() +
  theme(legend.position="none", 
        axis.text.x = element_text(size = 12), 
        axis.title = element_text(size = 14), 
        axis.text.y = element_text(size = 12)) + 
  labs(y = "Percent (%)", 
       x = "All reasons for non-vaccination: MSF") +
  scale_x_discrete(labels = function (reasons_msf) str_wrap(reasons_msf, width = 9)) # wrapping axis text with long labels  


table(study_data_cleaned$msf_all_reasons)

```


```{r No vaccination - Routine reasons}

# routine reasons
routine_all_reasons <- survey_design %>% 
  ## filter for not vaccinated 
  filter(str_detect(routine_vacc_status, pattern = fixed("Yes"), negate = TRUE)) %>%
  tab_survey(route_all_reasons) %>% 
  ## rename remaining columns appropriately 
  select("reason_routine" = value, 
         "Children (n)" = n,
         "Percent (95% CI)" = ci) %>%
  mutate(prop = `Children (n)`/sum(`Children (n)`)*100) %>% # using this column for graphing later
  mutate(prop = round(prop, 1))
  
#print table,arranged in descending order
routine_all_reasons %>%
  arrange(desc(prop))%>% 
  flextable() %>%
  autofit()

# graph of the routine reasons for non-vaccination (including OTHER, recoded. column created in chunk 17);
routine_all_reasons %>%
    ggplot(aes(x = reorder(reason_routine, -prop), y = prop, fill = reason_routine)) +
  geom_bar(stat ='identity') +
  scale_fill_viridis_d(begin = 0.7, end = 0.3) + 
  theme_classic() +
  theme(legend.position="none", 
        axis.text.x = element_text(size = 9), 
        axis.title = element_text(size = 12)) + 
  labs(y = "Percent (%)", 
       x = "All reasons for non-vaccination: routine") +
  scale_x_discrete(labels = function (reason_routine) str_wrap(reason_routine, width =9)) # wrapping axis text with long labels
    

#just number of children who did not receive vaccination
table(study_data_cleaned$routine_vacc_status)
table(study_data_cleaned$route_all_reasons)
table(study_data_cleaned$reason_route_other)
table(study_data_cleaned$reason_route_vacc)




```




```{r No vaccination - SIA reasons}

##sia reasons
sia_all_reasons <- survey_design %>% 
  ## filter for not vaccinated 
  filter(str_detect(sia_vacc_status, pattern = fixed("Yes -"), negate = TRUE)) %>%
  tab_survey(sia_all_reasons) %>% 
  ## rename remaining columns appropriately 
  select("reason_sia" = value, 
         "Children (n)" = n,
         "Percent (95% CI)" = ci) %>%
  mutate(prop = `Children (n)`/sum(`Children (n)`)*100) %>% # using this column for graphing later
  mutate(prop = round(prop, 1)) #going to use this column for ggplot since I can't separate the CI column easily. 


#print table
sia_all_reasons %>%
  arrange(desc(prop))%>% 
  flextable() %>%
  autofit()
  
# graph of SIA reasons for non-vaccination (including OTHER, recoded. column created in chunk 18);
sia_all_reasons %>%
    ggplot(aes(x = reorder(reason_sia, -prop), y = prop, fill = reason_sia)) +
  geom_bar(stat ='identity') +
  scale_fill_viridis_d(begin = 0.7, end = 0.3) + 
  theme_classic() +
  theme(legend.position="none", 
        axis.text.x = element_text(size = 10), 
        axis.title = element_text(size = 12)) + 
  labs(y = "Percent (%)", 
       x = "All reasons for non-vaccination: SIA") +
  scale_x_discrete(labels = function (reason_sia) str_wrap(reason_sia, width = 10)) # wrapping axis text with long labels
  

#just number of children who did not receive SIA vaccination
table(study_data_cleaned$sia_vacc_status)
table(study_data_cleaned$sia_all_reasons)


```



## Previous measles illness 

```{r previous measles,warning = FALSE, echo = FALSE}

# need to convert ages to one tyoe of format (chose to make all ages in years)
study_data_cleaned <- study_data_cleaned %>%
  mutate(diagnosis_age_new = case_when(
    age_diagnosis_months == 2 ~ 0.17,
    age_diagnosis_months == 3 ~ 0.25,
    age_diagnosis_months == 4 ~ 0.33,
    age_diagnosis_months == 5 ~ 0.42,
    age_diagnosis_months == 6 ~ 0.5,
    age_diagnosis_months == 7 ~ 0.58, 
    age_diagnosis_months == 8 ~ 0.67, 
    age_diagnosis_months == 9 ~ 0.75, 
    age_diagnosis_months == 10 ~ 0.83,
    age_diagnosis_months == 11 ~ 0.92, 
    age_diagnosis_years == 1 ~ 1, 
    age_diagnosis_years == 2 ~ 2, 
    age_diagnosis_years == 3 ~ 3, 
    age_diagnosis_years == 4 ~ 4, 
    age_diagnosis_years == 5 ~ 5, 
    age_diagnosis_years == 6 ~ 6,
    age_diagnosis_years == 7 ~ 7,
    age_diagnosis_years == 8 ~ 8,
    age_diagnosis_years == 9 ~ 9))

# median age child got sick
medage <- study_data_cleaned %>%
  filter(!is.na(diagnosis_age_new)) %>%
  select(diagnosis_age_new)

median(medage$diagnosis_age_new)

# number of children missing info on age they got sick
fmt_count(study_data_cleaned, is.na(diagnosis_age_new))

# previous disease history
survey_design %>%  # use the survey object (weighted)
  ## calculate weighted counts and weighted proportions
  tab_survey(diagnosis_disease, deff = TRUE) %>%
  ## select and rename appropriate columns 
  select("Previous measles diagnosis" = value, 
         "Children (n)" = n, 
         "Percent (95% CI)" = ci,
         "Design effect" = deff) %>%
  flextable () %>%
  colformat_num(col_keys = c("Design effect"), digits = 1) %>%
  autofit

#just number of children with previous diagnosis to fill in chart: 
study_data_cleaned %>%
  tab_linelist(diagnosis_disease)


```



Of the children who reported previously having measles, `r fmt_count(study_data_cleaned, is.na(diagnosis_age_new))` were missing information on the age the child became ill. 


```{r measles immunity}


#just count of children for table: 
study_data_cleaned %>%
  tab_linelist(immunity)

survey_design %>%  # use the survey object (weighted)
  ## calculate weighted counts and weighted proportions
  tab_survey(immunity, deff = TRUE) %>%
  ## select and rename appropriate columns 
  select("Immune status" = value, 
         "Children (n)" = n, 
         "Immunity (95% CI)" = ci,
         "Design effect" = deff) %>%
  flextable () %>%
  colformat_num(col_keys = c("Design effect"), digits = 1) %>%
  autofit



```








